### 2011-04-03 acronym.tex
second commit

\section*{Acronyms}
\begin{acronym}
%\acronym{JDT}{\emph{Java Development Tools}}
%\acronym{NFC}{\emph{Number of Function Calls}}
\setlength{\itemsep}{-\parsep} 
\acro{SP}[SP]{Standardized Patient}
\acro{SPs}[SPs]{Standardized Patients}
\acro{etext}[e-text]{electronic text}
\acro{pdf}[PDF]{Portable Document File}
\acro{CSVs}[CSVs]{Comma Separated Values }
\acro{ttcn3}[TTCN-3]{Test and Test Control Notation Version 3}
\acro{ttcn}[TTCN]{Tree and Tabular Combined Notation}
\acro{etsi}[ETSI]{European Telecommunications Standards Institute}
\acro{itut}[ITU-T]{International Telecommunication Union}
\acro{3gpp}[3GPP]{Third Generation Partnership Project}
\acro{ims}[IMS]{Ip Multimedia Systems}
\acro{itut}[ITU-T]{International Telecommunication Union}
\acro{iso}[ISO]{International Organization for Standardization}
\acro{sut}[SUT]{System Under Test}
\acro{api}[API]{Application Programming Interfaces}
\acro{3g}[3G]{Third Generation}
\acro{ast}[AST]{Abstract Syntax Tree}
\acro{asts}[ASTs]{Abstract Syntax Trees}
\acro{tci}[TCI]{Test Control Interface}
\acro{tri}[TRI]{Test Runtime Interface}
\acro{mtc}[MTC]{Main Test Component}
\acro{ptc}[PTC]{Parallel Test Component}
\acro{antlr}{Another Tool for Language Recognition}
\acro{trex}[TRex]{TTCN-3 Refactoring and Metrics Tool}
\acro{dot}[DOT]{Drawing of Directed Graphs}
\acro{uml}[UML]{Unified Modeling Language}
\acro{csv}[CSV]{Comma-Separated Values}
\acro{tle}[TLE]{Top Level Element}
\acro{tlecand}[TLEcand]{Top Level Element Candidate}
\end{acronym}

### 2011-04-03 paper.tex
second commit

%% This is file `elsarticle-template-1-num.tex',
%%
%% Copyright 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%%
%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $
%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
%%
\documentclass[preprint,authoryear,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

\usepackage[printonlyused]{acronym}

\usepackage{color}

\newcounter{countNotes}
\newcommand{\annKB}[1]{\color{blue}*\textsuperscript{\thecountNotes}\marginpar{\color{blue} \tiny *\textsuperscript{\thecountNotes}\textbf{Note (KB): \\}
    #1  }\addtocounter{countNotes}{1}\color{black}}
%\renewcommand{\annKB}[1]{} %disable annotation

% \renewcommand{sbw}{} %disable comments

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

\journal{has to be discussed}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Development and Data Collection of a Facebook application}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author[focal]{Kathrin Becker\corref{cor1}\fnref{fn1}} 
\ead{mail@kathrin-becker.eu}
\author[focal]{Mayutan Arumaithurai\fnref{fn1}} %
\ead{mayutan.arumaithurai@gmail.com}
\author[focal]{Xiaoming Fu\corref{cor2}\fnref{fn1}} %
\ead{fu@cs.uni-goettingen.de}

\address[focal]{Institute of Computer Science, Computer Networks (NET)
  Research Group, University of G\"ottingen}

\cortext[cor1]{Corresponding author}
\cortext[cor2]{Principal corresponding author}
\fntext[fn1]{This document is a collaborative effort.}
%\fntext[fn2]{Another author footnote, but a little more longer.}
%\fntext[fn3]{Yet another author footnote. Indeed, you can have
%xany number of author footnotes.}
\tnotetext[tn1]{This is a specimen title.}

\begin{abstract}
%% Text of abstract, 150 - 350 words
% The outcome was students' perceptions of preparedness.

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
Facebook, Social Networking, data mining, social graph
\end{keyword}

\end{frontmatter}

%%

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix
%% main text
%% Start line numbering here if you want
%%
%o \linenumbers

\section{Introduction}
\label{sec:introduction}

\section{Methodology}
\label{sec:method}

% Describes:
% \begin{itemize}
% \item Probands (studied objects): Type, number, characteristics, age,
% gender by arithmetic means and distribution
% \item materials: surveys (exemplary demonstration!) incl instructions, software used, given media (differences)
% \item Proceeding: Splitting of the group, quality of questions
% \item Evaluationmethods: methods used for evaluation (statistical tests)
% \end{itemize}

\section{Results}
\label{sec:results}

\begin{center}
\begin{table}
\label{tab:coruser}
\begin{tabular}{l | c c c}
a & a & a & a \\

\hline
b & b & b & b
\end{tabular}
\caption{dummy}
\end{table}
\end{center}

\section{Discussion}
\label{sec:discussion}

\section{Outlook}
\label{sec:outlook}

\section{Conclusion}
\label{sec:conclusion}

\include{acronym} % load acronyms
%% \section{}
%% \label{}

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}          ==>>  [#]
%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
%%   \citet{key}         ==>>  Author [#]

%% References with bibTeX database:

\bibliographystyle{elsarticle-harv}
\bibliography{literature.bib}

%% Authors are advised to submit their bibtex database files. They are
%% requested to list a bibtex style file in the manuscript if they do
%% not want to use model1-num-names.bst.

%% References without bibTeX database:

% \begin{thebibliography}{00}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

% \bibitem{}

% \end{thebibliography}

\end{document}

%%
%% End of file `elsarticle-template-1-num.tex'.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2011-04-07 paper.tex
asbtract basics and intro draft version

@@
 %%
-\documentclass[preprint,authoryear,12pt]{elsarticle}
+\documentclass[preprint,12pt]{elsarticle}
 
@@
 %% \usepackage{amsthm}
+\usepackage{hyperref} %\url can be used, links are highlited
 
@@
 \usepackage{color}
+\usepackage{xcolor}
+
+\usepackage{listings} \lstset{numbers=left, numberstyle=\tiny,
+  basicstyle=\footnotesize, stepnumber=2, numbersep=5pt,
+  showspaces=false, showstringspaces=false, frame=single,
+  breaklines=true,
+  backgroundcolor=\color{white},morekeywords={id,gender, name,
+    first_name, username, gender, locale},
+  numbersep=5pt} \lstset{language=Perl}
 
@@
 
-\title{Development and Data Collection of a Facebook application}
+\title{Distribution of a Facebook application}
 
@@
 % The outcome was students' perceptions of preparedness.
+This paper investigates, how a small Facebook application 
+distributes among friends. A graph is created which represents users, who
+installed the application, as nodes and friendship between them as
+edges. In addition, metrics are calculated to determine, which
+parameters  make users likely to invite their friends to
+participate.
 
+The application itself is a quiz which asks people 5
+questions, randomly selected from a pool of 20 questions, 
+about dentistry health facts. After the quiz, participants
+get to know if they had a higher score than their friends and who of their
+friends answered the questions they got correctly.
+
+Results show users, who yield a high score in the quiz,
+more likely to invent other users than users, who got a worse
+score. In addition, the number of friends did not mark users to be
+relevant for spreading the app. Indeed, people who had less friends
+were much more likely to spread the application.
 \end{abstract}
@@
 \label{sec:introduction}
+Founded in 2004, Facebook\footnote{www.facebook.com} has
+become a social network currently used by more than 600 million people
+all over the world\cite{facebook500}. Since 2007, Facebook provides an API allowing
+third party developers to embed their own applications into
+Facebook\footnote{http://developers.facebook.com/blog/archive}.
+Subsequent to the F8 conference in April, 2010, Facebook simplified
+access to its social graph via Open Graph Protocol \cite{facebookStats} and allowed
+for integration of external websites. Until October, 2009,
+over 350 000 apps had been seen on Facebook \cite{facebookBlog}.
+Due to current statistics, people install about 20 million apps per day. In addition, ten thousand new
+websites integrate with Facebook every day. \cite{facebookStats}
+
+Due to integration in Facebook's social graph, third party
+applications spare user authentication procedures and can access
+private user information as well. These information can include basic
+information and friend lists, but also interests and further data
+specified by an access token  \footnote{http://developers.facebook.com/docs/authentication/}.
+As the data provided by Facebook, and collected by analyzing user
+behaviour on an application, represent a lot of social information, it
+seems obvious, that these data also allow for studying social groups.
+
+This paper investigates the distribution process of a quiz on Facebook
+by analysing which parameters make users likely to distribute the application
+and which parameters do not.
+
+In the first section, background information
+about how applications can be integrated with Facebook are
+given. Then, the methodology is described in section \ref{sec:method},
+including the quiz, as well as the 
+proceedings used for data collection and evaluation. In section
+\ref{sec:results}, the results are detailed, and in section
+\ref{sec:discussion} and \ref{sec:outlook}, they are discussed and an
+outlook is given for further research.
+
+\section{Background}
+\label{sec:background}
+This section describes the social graph concept, how applications can be integrated with
+Facebook, how authentication and authorisation is done, and in which
+format data from the social graph can be obtained.
+
+\subsection{Social Graph}
+\label{sec:social-graph}
+The \textit{social graph} is at Facebook's core. It represents
+connections between people and things they care about
+\cite{facebookDev}. In April, 2010, Facebook included access to the
+social graph via the Open Graph Protocol, which advanced integration of
+external websites into the social graph \cite{facebookDev2}. These websites can make use of
+social plugins such as \textit{Like Buttons} or \textit{Comment Boxes} \cite{facebookDev2}
+and for this reason, the social graph contains not only connections between
+people on Facebook (friend relations), but also between 
+entities such as applications, movie entries on external websites,
+news articles, and much more. As this allows
+people to identify friends on external websites and receive
+information about their friends' attitude towards anything their
+friends have visited and commented before, one can say
+that Facebook's social graph makes the Internet social.
+
+The Graph API is one of Facebook's core concepts and presents a consistent
+view of the social graph. Every object has an unique ID and its
+properties can be accessed by requesting the appropriate URL:
+\url{https://graph.facebook.com/ID}. Listing \ref{list:kbecker} shows
+the author's public user node on Facebook's social graph. which is
+returned as a \ac{json}-object\footnote{http://www.json.org}.
+
+\begin{lstlisting}[caption=JSON object from
+  \url{https://graph.facebook.com/681178092},
+  label=list:kbecker]{}
+{
+   "id": "681178092",
+   "name": "Kathrin Becker",
+   "first_name": "Kathrin",
+   "last_name": "Becker",
+   "username": "kathrin.becker1",
+   "gender": "female",
+   "locale": "de_DE"
+}
+\end{lstlisting}
+
+In order to get access not only to public, but also to private
+information, an access token has to be included in the Graph API
+request. To get this token, the accessing entity must be
+authorized and authenticated to do so. How this can be achieved is
+discussed in section \ref{sec:auth-auth}. If one tries to access
+non-public information such as the author's list of friends, an error
+in terms of a missing access token is returned. An example is given in
+listing \ref{list:kbeckerfriends}.
+
+\begin{lstlisting}[caption=JSON object from
+  \url{https://graph.facebook.com/681178092/friends},
+  label=list:kbeckerfriends]{}
+{
+   "error": {
+      "type": "OAuthException",
+      "message": "An access token is required to request this resource."
+   }
+}
+\end{lstlisting}
+
+Besides the Graph API, Facebook's social graph can also be accessed
+with the REST-API, which is in the processes of deprecating
+\cite{facebookDev3}. Both, the Graph API and the REST-API support
+O-Auth 2.0 for authentication and authorization. O-Auth 2.0 is
+included in Facebook's \ac{sdks} (see section
+\ref{sec:integr-appl-with} and \ref{sec:auth-auth}).
+
+\subsection{Integration of Applications with Facebook}
+\label{sec:integr-appl-with}
+Applications on Facebook are hosted on external severs, and are loaded
+into a \textit{Canvas Page} by using iFrames. After registration
+(\url{http://www.facebook.com/developers/createapp.php}), applications
+can be found under the URL \url{http://apps.facebook.com/your_app }.
+As soon as the application exists for some month and has
+some users registered, it can be added to Facebook's application
+index.
+
+Facebook provides several features to support the development
+process. \ac{sdks} exist for popular programming languages and provide
+sets of pre-defined functions for communication with Facebook. For
+instance, they include the O-Auth 2.0 dialog which is described in
+section \ref{sec:auth-auth}. In
+addition, Facebook grants observation of its own development process by
+making its raodmap public, and by showing its buglist. In addition, a
+testserver exists to help developers to analyze if their application
+is going to run with planned features from Facebook. 
+Facebook provides an \textit{insights}-feature which makes
+statistics about the applications available. \cite{oreilly}.
+
+\subsection{Authentication and Authorization}
+\label{sec:auth-auth}
+In order to authorize and authenticate, Facebook recommends usage of
+O-Auth 2.0 protocol by using the OAuth Dialog included in its
+\ac{sdks}. As the application analyzed in this paper and described in section 
+\ref{sec:method} implements the O-Auth Dialog from the PHP-\ac{sdk},
+this variant will be described in detail. It shall just be mentioned,
+that Facebook also allows for manual execution of the steps to receive
+access tokens.\cite{facebookDevAuth}
+
+The OAuth Dialog performs three steps, i.e. user authentication, 
+and authorization as well as authentication of the
+application. If these three steps are completed, the application is
+issued an \textit{user access token}. If more than basic information
+is needed from Facebook, scope parameters can be set.\cite{facebookDevAuth}
+
+Figure \ref{fig:authorization} details how authorization and
+authentication take place with OAuthDialog. The \textit{app server}
+show cases the server on which the app is actually
+running. \textit{Facebook} represents all the Facebook servers, on
+which perform authentication and authorization. The \textit{OAuth
+  Dialog} runs on the browser of the client who is going to use the
+application.
+
+\begin{figure}
+\label{fig:authorization}
+  \includegraphics[width=4in]{../img/fbinteraction3.png}
+  \caption{Facebook establishes trust relation by not sending login
+    data to app server, but using access tokens instead for
+    data exchange with app server.}
+\end{figure}
+
+When clients access the canvas page of the application, they are
+redirected to the OAuth Dialog (running on a Facebook server) and
+provided with the application's ID. Then, user authentication and
+app authorization is performed, by involving the client and Facebook
+only. User authentication is done by logging in on Facebook (if necessary) and
+authorization of the application is done by asking the user if he/she
+wants to grant the application access to some data specified by the
+application with the scope parameter. One should note, that no
+login data are sent to the application, thus, this is how Facebook
+establishes a trust relation. 
+If the user authorizes the application, an \textit{authorization code} is returned and
+the user is redirected to the application, to which the
+\textit{authorization code} is forwarded. When registering the
+application, an \textit{application secret} code has been
+created. In order to authenticate the application, the
+\textit{authorization code} and the \textit{application secret} have
+to be sent to Facebook's \textit{Graph API Token Endpoint}. Facebook
+then returns an \textit{access token}, which can be included in the
+URL by which the Graph API can be accessed. However, Facebook's
+\ac{sdks} also provide functions to perform calls to the Graph API,
+and in this case, the access token is included automatically.
+
+\subsection{Data from social graph (JSON-Objects)}
+\label{sec:json-objects}
 
@@
 
-% Describes:
-% \begin{itemize}
-% \item Probands (studied objects): Type, number, characteristics, age,
-% gender by arithmetic means and distribution
-% \item materials: surveys (exemplary demonstration!) incl instructions, software used, given media (differences)
-% \item Proceeding: Splitting of the group, quality of questions
-% \item Evaluationmethods: methods used for evaluation (statistical tests)
-% \end{itemize}
+\subsection{The Quiz}
+\label{sec:quiz}
+
+\subsection{Data collection and evaluation}
+\label{sec:data-coll-eval}
 
@@
 
-\section{Conclusion}
-\label{sec:conclusion}
+%\section{Conclusion}
+%\label{sec:conclusion}
 

### 2011-04-08 paper.tex
methodology

@@
 authentication take place with OAuthDialog. The \textit{app server}
-show cases the server on which the app is actually
+illustrates the server on which the app is actually
 running. \textit{Facebook} represents all the Facebook servers, on
@@
 
-\subsection{Data from social graph (JSON-Objects)}
-\label{sec:json-objects}
-
 \section{Methodology}
 \label{sec:method}
+In this section, the quiz is described as well as its
+implementation. Then, it is explained how data are collected for
+further analysis and how they can be evaluated.
 
@@
 \label{sec:quiz}
+The quiz contains questions in German about dentistry health facts. Participants are asked 5
+questions taken from a pool of 20 questions. Each question has 4
+possible answers. Multiple selection is possible, but at least one
+answer is correct. A question is answered correctly, if each correct
+and no incorrect answer have been selected. Figure \ref{fig:quiz}
+shows how the quiz looks like.
 
-\subsection{Data collection and evaluation}
+\begin{figure}
+  \includegraphics[height=3in]{../img/fbquiz.png}
+ \caption{The quiz.}
+\label{fig:quiz}
+\end{figure}
+
+The quiz is competitive. After the quiz is completed, user are told
+how good they were in comparison to other participants and to their
+friends. As shown in figure \ref{fig:solution}, for each question the
+correct solution is given. A user can also invite friends to
+participate by clicking on the appropriate image. This is demonstrated in
+figure \ref{fig:invite}.
+
+\begin{figure}
+  \includegraphics[width=3.5in]{../img/fbsolution.png}
+  \caption{Solution of a question.}
+\label{fig:solution}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=3.5in]{../img/fbinvite.png}
+  \caption{This screenshot shows how friends can be invited.}
+\label{fig:invite}
+\end{figure}
+
+\subsection{Implementation}
+\label{sec:implementation}
+The quiz-application detailed in the last section makes use of
+Facebook's php-\ac{sdk} and JavaScript-\ac{sdk}. It requires
+permissions for \textit{user$\_$birthday} and \textit{publish$\_$stream}.
+Data used by the quiz are stored in a MySQL-database, tables have the
+following contents:
+\begin{itemize}
+\item \textbf{User} - entries are created for each user who participates as
+well as for each of a user's friends. A flag details if user
+participated or not.
+\item \textbf{Friendships} - creates entries for each friendship found in
+users' friend lists.
+\item \textbf{Questions} - contains the questions of the quiz.
+\item \textbf{Answers} - contains the possible answers and a flag to mark them
+as correct or false.
+\item \textbf{Given answers} - stores each answer given by a user.
+\item \textbf{User score} - stores the score user had in the quiz.
+\item \textbf{Correct answered questions} - stores which questions were correct
+answered by which user.
+\end{itemize}
+
+The database queries are performed with the PHP
+pear\footnote{http://pear.php.net/}-package. The script which performs
+the queries uses few files: The index.php manages the application
+flow. The library.php contains all the functions needed, and quiz.php,
+question.php, and quizResult.php display the quiz as well as the
+correct solution and the feature to invite friends.
+
+\subsection{Data collection}
 \label{sec:data-coll-eval}
+
+\subsection{Data evaluation}
+\label{sec:data-evaluation}
 
@@
 
-\begin{center}
-\begin{table}
-\label{tab:coruser}
-\begin{tabular}{l | c c c}
-a & a & a & a \\
+% \begin{center}
+% \begin{table}
+% \label{tab:coruser}
+% \begin{tabular}{l | c c c}
+% a & a & a & a \\
 
-\hline
-b & b & b & b
-\end{tabular}
-\caption{dummy}
-\end{table}
-\end{center}
+% \hline
+% b & b & b & b
+% \end{tabular}
+% \caption{dummy}
+% \end{table}
+% \end{center}
 

### 2011-04-08 paper.tex
implementation and data evaluation

@@
 Facebook's php-\ac{sdk} and JavaScript-\ac{sdk}. It requires
-permissions for \textit{user$\_$birthday} and \textit{publish$\_$stream}.
-Data used by the quiz are stored in a MySQL-database, tables have the
-following contents:
+permissions for \textit{user$\_$birthday} and
+\textit{publish$\_$stream}.
+Data used by the quiz are stored in a MySQL-database, and php scripts
+handle the application flow. \textit{index.php} maintains calls of
+scripts printing the quiz (\textit{quiz.php}, \textit{question.php}), and displaying
+the correct solution as well as the opportunity to invite friends
+after completion of the quiz
+(\textit{quizResult.php}). \textit{library.php} contains all the
+functions needed.
+
+\subsubsection{Database schema}
+\label{sec:database-schema}
+The database queries are performed with PHP
+pear\footnote{http://pear.php.net/}-package. The following tables exist:
 \begin{itemize}
@@
 participated or not.
-\item \textbf{Friendships} - creates entries for each friendship found in
+\item \textbf{Friends} - creates entries for each friendship found in
 users' friend lists.
@@
 as correct or false.
-\item \textbf{Given answers} - stores each answer given by a user.
-\item \textbf{User score} - stores the score user had in the quiz.
-\item \textbf{Correct answered questions} - stores which questions were correct
-answered by which user.
+\item \textbf{GivenAnswers} - stores each answer given by a user.
+\item \textbf{UserScore} - stores the score user had in the quiz.
+\item \textbf{CorrectAnsweredQuestions} - stores which questions were correct
+answered by which user, and which were not.
 \end{itemize}
 
-The database queries are performed with the PHP
-pear\footnote{http://pear.php.net/}-package. The script which performs
-the queries uses few files: The index.php manages the application
-flow. The library.php contains all the functions needed, and quiz.php,
-question.php, and quizResult.php display the quiz as well as the
-correct solution and the feature to invite friends.
+\subsubsection{Application flow}
+\label{sec:application-flow}
+When a user enters, the \textit{OAuth Dialog} is started. Then, the user data
+including gender, birthday, name, Facebook-ID are stored together with
+a timestamp, and column \textit{has-used-app} is set to 1. In
+addition, each user's friends are also stored and column
+\textit{has-used-app} is set to 0. Then, friendships are stored in the
+table \textit{friends}. Next, the quiz is created by randomly choosing
+five questions from the questions table and requiring the answers. To
+make the questions more attractive, the name of an image convenient to
+the questions topic is also stored in the questions table, and this
+image is placed on the left side of each question. Since multiple
+selection is possible, before the answers, which are also queried from
+the MySQL database, checkboxes are placed before each answer.
 
-\subsection{Data collection}
-\label{sec:data-coll-eval}
+As soon as a user completed the quiz, evaluation starts by checking
+which questions were answered correctly and by computing the final
+score. Due to multiple selection, user answers are stored in
+an multidimensional array and compared with another multidimensional
+array containing the correct solution and created from the database.
+The given answers are then stored, and in addition, in another table
+(\textit{correctAnsweredQuestions)}
+it is only stored which questions were correct and incorrect answered.
+Some user join the quiz multiple times, and for this reason, each
+score they had is stored in a score table. The user table is also
+changed by entering or updating the average score, computed from each all the scores stored
+in the score table. Then, by using the Java Script \ac{sdk}, the user
+get the option to post the results onto their Facebook wall.
+
+In order to make the whole thing challenging, it
+is then computed how high the user's score is compared to the friends
+and to all the other users. 
+In addition, the correct solutions are given, and if a user knew the
+right answer, a green check is placed left to the question. Otherwise,
+a red cross is displayed at the same place. At least, the table with
+the friendships and table \textit{correctAnsweredQuestions} are used
+to identify friends  which answered the question correctly. Images of
+them are placed beyond each question's solution together with the
+information that those friends knew the right solution. 
+In the end, users get the chance to invite friends to the app to
+challenge them. For this reason, each friend's picture is added and
+user can click at them. On click, a pre-defined function from
+Facebook's Java Script \ac{sdk} is called to perform the invitation.
 
@@
 \label{sec:data-evaluation}
+Data evaluation is also performed by using the MySQL tables, and
+PHP. In addition, the dot
+language\footnote{http://www.graphviz.org/Documentation.php} is used
+to create graphs.
+
+The evaluation scripts are maintained by \textit{main.php}. A user
+class represents Facebook's social graph internally. Properties of
+user objects equal the \textit{user}-table's properties, and a user's
+friendships are represented by a list of references to corresponding
+user objects. The whole set of users is maintained by
+\textit{main.php}, where they are stored in an array. Class \textit{Graph}
+allows for output of various graphs in dot-language created from the
+internal social graph.
 

### 2011-04-10 paper.tex
first version completed

@@
 the user is redirected to the application, to which the
-\textit{authorization code} is forwarded. When registering the
-application, an \textit{application secret} code has been
+\textit{authorization code} is forwarded. During registration of the
+application, an \textit{application secret} code was
 created. In order to authenticate the application, the
@@
 and in this case, the access token is included automatically.
+
+\subsection{Graphs with DOT language}
+\label{sec:graph-repr-with}
+The \ac{dot} language allows for plain text description of
+graphs. There are few programs that can process \ac{dot} graphs, most
+of them are part of the
+\textit{Graphviz}\footnote{http://www.graphviz.org}-package. 
+The language allows for directed and undirected graphs, attributes can
+be set and colors as well as different shapes for nodes and edges can
+be used. The basic syntax is very easy, the graph shown in figure
+\ref{fig:dot} has the \ac{dot}-code given in listing \ref{list:dot}.
+
+\begin{lstlisting}[caption=A very simple DOT-Graph,
+  label=list:dot]{}{
+ digraph myGraph {
+     a -> b;
+}
+\end{lstlisting}
+
+\begin{figure}
+  \includegraphics[width=0.4in]{../img/ab.png}
+\caption{A very simple graph in \ac{dot}-language.}
+\label{fig:dot}
+\end{figure}
+
+Labels and colors can be added by defining the node in the head of the
+graph description. An example is detailed in listing \ref{list:dot2}, and
+the corresponding graph is given in figure \ref{fig:dot2}.
+
+\begin{figure}
+  \includegraphics[width=0.4in]{../img/graphDot.png}
+\caption{A very simple graph with node a blue boxed and fontcolor set
+  to red.}
+\label{fig:dot2}
+\end{figure}
+
+\begin{lstlisting}[caption=A very simple DOT-Graph,
+  label=list:dot2]{}{
+ digraph myGraph {
+a [label="Foo", color="blue", shape=box, fontcolor="red"];
+     a -> b;
+}
+\end{lstlisting}
 
@@
 figure \ref{fig:invite}.
-
-\begin{figure}
-  \includegraphics[width=3.5in]{../img/fbsolution.png}
-  \caption{Solution of a question.}
-\label{fig:solution}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=3.5in]{../img/fbinvite.png}
-  \caption{This screenshot shows how friends can be invited.}
-\label{fig:invite}
-\end{figure}
 
@@
 \label{sec:data-evaluation}
-Data evaluation is also performed by using the MySQL tables, and
+Data evaluation is performed by using the MySQL tables, and
 PHP. In addition, the dot
@@
 The evaluation scripts are maintained by \textit{main.php}. A user
-class represents Facebook's social graph internally. Properties of
-user objects equal the \textit{user}-table's properties, and a user's
-friendships are represented by a list of references to corresponding
-user objects. The whole set of users is maintained by
-\textit{main.php}, where they are stored in an array. Class \textit{Graph}
-allows for output of various graphs in dot-language created from the
-internal social graph.
+class represents Facebook's social graph internally. Its properties
+are user's Facebook ID, registration date, average score, a list of
+friends, and a list of IDs to whom the user may have spread the
+application. Friendships are represented by a list of references to corresponding
+user objects, and names of users' can be made anonymous if needed.
+
+A user is supposed to have spread the app if he/she has
+a friend who used the application and who belongs to a \textit{new}
+network. Such persons are found by recursively checking if an user of
+the application has friends, who also used the application, and whose friends
+also used the app, but are not in his/her list of friends, and also not in the list of the person
+who originally spread the application. In this case, the corresponding
+friend will be marked as a person who spread the application, and the
+recursion starts by letting the friend become the analyzed user.
+Since it is not clear, why a person started to use an application, the
+script also allows for identification of users who have friends 
+who also participated in the application.
+
+User names are made anonymous by substituting their names with a
+random name selected from a list of popular baby names
+from 2009, taken from \url{http://www.ssa.gov/cgi-bin/popularnames.cgi}.   
+For each gender, hundred names are stored in an array, and if the
+gender is set, a name of same gender is chosen. Otherwise, the name is
+taken randomly. The name of the person who spread the application
+originally is always set to \textit{Alexandra}.
+
+Output options are a \ac{csv}-file containing metrics calculated from
+the internal social graph as well as various graphs in dot language, created
+from the internal social graph, too.
+% Properties of
+% user objects are in the style of the \textit{user}-table's properties, and a user's
+% . The whole set of users is maintained by
+% \textit{main.php}, where they are stored in an array. Class \textit{Graph}
+% allows for output of various graphs in dot-language created from the
+% internal social graph.
 
@@
 \label{sec:results}
+A total of n=48 users participated in the quiz. 5505 users have been
+stored in the user table. Thus, on average each user brought on
+average 114.7 \textit{new} people, who could read about the application
+in their news stream. 15
+
+\subsection{Characteristics}
+\label{sec:characteristics}
+
+The characteristics discussed in this section consider data of users
+that are still registered (n=37).
+
+\subsubsection{Age and gender}
+\label{sec:age-gender}
+$59 \%$ of the registered user are female, $41 \%$ of the participants
+are male. Table \ref{tab:agegender} shows classification of the users
+by age and gender. It can be seen, that most users ( 70 \%) were at
+the age of 25-34. Only few ($8.4 \%$) were older, and only 21.4 \%
+were younger.
+
+\begin{center}
+\begin{table}
+\label{tab:agegender}
+\begin{tabular}{l | c c c c}
+Gender\textbackslash Age  & 13-17 & 18-24 & 25-34 & 45-54 \\
+\hline
+female  & 2.7 \% & 16 \% & 35 \% & 5.4 \% \\
+male & 0 \% & 2.7 \% & 35 \% & 2.7 \% 
+\end{tabular}
+\caption{Table shows classification of users by age and gender.}
+\end{table}
+\end{center}
+
+\subsubsection{Demography}
+\label{sec:demographie}
+Table \ref{tab:countries} details the origin of the users and table
+\ref{tab:languages} the languages in which the participants use Facebook.
+As it seems obvious for a quiz in German, most visitors came from Germany.
+
+\begin{center}
+\begin{table}
+\label{tab:countries}
+\begin{tabular}{l | c }
+Country  & Visitors \\
+\hline
+Germany  & 32 \\
+United Kingdom & 2 \\
+Israel & 1 \\
+United States of America & 1 \\
+Austria & 1 \\
+\end{tabular}
+\caption{Table shows where the users are from.}
+\end{table}
+\end{center}
+
+\begin{center}
+\begin{table}
+\label{tab:languages}
+\begin{tabular}{l | c }
+Languages   & Visitors \\
+\hline
+German  & 25 \\
+English (UK) & 7 \\
+English (US) & 4 \\
+Greek  & 1 \\
+\end{tabular}
+\caption{Languages of the participants.}
+\end{table}
+\end{center}
+
+\subsection{Spreading of the quiz}
+\label{sec:distribution-quiz}
+In this section, graphs illustrating how the
+application spread are presented. The original user names collected from Facebook were made anonymous
+before the graphs were printed (see section \ref{sec:data-evaluation}). Friendships are
+represented by directed edges: If user A has user B in the friend list, an
+arrow exists targeting user B.
+
+Figure \ref{fig:allUsers} represents each user stored in user
+table as node, and friendships of those who participated in the
+application as directed edges. Names of users who participated in the quiz are distinguished by
+red font color. The main purpose of this figure is to visualize the
+whole setting and to give an imagination of how many \textit{new}
+people on Facebook could have read about the application in their 
+news stream. In addition, the figure shows few participants, who are
+not connected to the larger network of the 
+person who started to spread the application.
+
+\begin{figure}
+  \includegraphics[width=5.2in]{../img/allUserTree.png}
+\caption{Figure shows all users stored in the database. Users who
+  participated have a red text color.}
+\label{fig:allUsers}
+\end{figure}
+
+In the following, only user who participated in the quiz are
+considered. In Figure \ref{fig:spreading} nodes of people, who are
+connector between two networks, have a red font color. The number of
+friends and the average score from quiz are also shown. 
+It can be obtained that in three cases, there are several connections (friendships)
+between the people who participated and belong to a new network. For
+instance, several connections exist between users \textit{Evan},
+\textit{Diego}, \textit{Isabelle}, \textit{Chase}, and \textit{Gebrielle}.
+\textit{Nicholas} and \textit{Chase}, who are friends with those
+people mentioned above, also are friends with \textit{Ethan},
+and \textit{Josiah}.  Then, \textit{Faith} is friend with
+\textit{Owen} and \textit{Colton}, who also know each other, and
+\textit{Mariah} and \textit{Sydney} have \textit{Alexis} as a common
+friend. The figure also shows that most people who spread the
+application had a score greater than or equal to three. At least, it
+can be obtained that half of the people who spread the application
+had less than hundred friends, which is less than the mean on
+Facebook, i.e. 130 friends \cite{ref:facebookStats}.
+
+In the addendum (section \ref{sec:addendum}), two further graphs are
+shown. In figure \ref{fig:friendsScored}, the background color
+represents a user's average score. User with a darker background had a
+higher score with those having a lighter background color. 
+Figure \ref{fig:friendsFilled} visualizes the amount of friends in the
+by giving users having many friends a dark and those having fewer
+friends a lighter background color.
+
+\begin{figure}
+  \includegraphics[width=5in]{../img/spreading.png}
+\caption{Figure shows all users stored in the database. Users who
+  participated have a red text color.}
+\label{fig:spreading}
+\end{figure}
+
+Two tables also located in the addendum describe to how many
+other participants friendships existed (see table \ref{tab:spread} and
+\ref{tab:nospread}), and to how many people of a
+\textit{new} network the application was (probably) distributed by the
+user. $26$ participants were on average $2.54$ friends with other
+participants and those, who spread the application, seemed to have
+more connections to other people than those who did not.
+The average score of people connected to others was $3.02$. It was
+higher than the average score of people not connected to others ($2.41$).
+People not connected to further participants had fewer friends on average ($106.8$)
+than the connected participants ($138.83$).
+
+Table \ref{tab:nouser} details how many friends who participated in
+the application user had, who did not participate in the
+application. Most times, those people just had one friend, but in eleven
+cases, they had four or five participants in their friends list.
+
+\begin{table}
+\label{tab:nouser}
+\begin{tabular}{c c}
+Number of friends & Frequency \\
+1& 5150\\
+2& 240\\
+3& 55\\
+4& 6\\
+5& 5\\
+\end{tabular}
+\caption{Table details how many friends user had, who did not
+  participate in the application.}
+\end{table}
 
@@
 
-\section{Discussion}
+\section{Discussion and Outlook}
 \label{sec:discussion}
+From the results given in section \ref{sec:results} it can be derived
+that the number of friends did not to play a bigger role in the
+process of the application's distribution. The number of connections
+to other users seems to play a bigger 
+role, as it is indicated by table \ref{tab:spread} and figure
+\ref{fig:spreaders}. In addition, a worse score made people unlikely
+to spread the application, just one person with a score less than 3
+did so. Thus, people with a higher score (on average $3.11$, median $3.32$) are
+supposed to have distributed the application. Indeed, some people who
+had four or five friends who participated in the application did not
+install the application.
 
-\section{Outlook}
-\label{sec:outlook}
+In order to get more reliability towards the processes of distribution
+of applications on Facebook, more applications must be analyzed.
+Future research may consider, how patterns change with respect
+to users' age, and if further characteristics can be identified. In
+case of larger applications, it could be studied, if turning points
+or intervals exist, which - when exceeded - make users significantly
+more likely to join the application.
 
-%\section{Conclusion}
-%\label{sec:conclusion}
+\section{Conclusion}
+\label{sec:conclusion}
+This research indicates, that the spreading of application follows
+certain patterns. Oftentimes, people say that they don't want to
+make a worse impression on Facebook, and this is also reflected in the
+fact, that only people who yield higher scores in the quiz also
+distributed to their friends. In the environment analyzed, dense
+networks with few participants, i.e. in networks in which people know
+each other, made  further members of their network very likely to join
+the application. Indeed, the number of friends did not play a role in
+making people likely to spread the application.
 
@@
 
+\newpage
+\section{Addendum}
+\label{sec:addendum}
+\begin{figure}
+  \includegraphics[width=3.5in]{../img/fbsolution.png}
+  \caption{Solution of a question.}
+\label{fig:solution}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=3.5in]{../img/fbinvite.png}
+  \caption{This screenshot shows how friends can be invited.}
+\label{fig:invite}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=5in]{../img/friendsScored.png}
+\caption{Figure shows all users stored in the database. Users who
+  participated have a red text color.}
+\label{fig:friendsScored}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=5in]{../img/friendsFilled.png}
+\caption{Figure shows all users stored in the database. Users who
+  participated have a red text color.}
+\label{fig:friendsFilled}
+\end{figure}
+
+ \begin{table}
+ \label{tab:spread}
+ \begin{tabular}{ c c c c}
+Friends & Score & Friends who also participated & Probably spread appl. to friends\\
+\hline
+97 & 3.33 & 1 &-\\
+322 & 1.5 & 4 & -\\
+63 & 4 & 1 & 1\\
+102 & 0 & 2 & -\\
+91 & 1 & 3 &1\\
+128 & 4 & 2 & -\\
+151 & 3 & 4 &3\\
+135 & 3.64 & 3 &2\\
+254 & 4 & 2 & 2\\
+220 & 3 & 4 & -\\
+127 & 3 & 2 & -\\
+186 & 4 & 3 & -\\
+42 & 3 & 4 & - \\
+445 & 3 & 4 & - \\
+153 & 3 & 2 &1\\
+20 & 3 & 1 &1\\
+11 & 4.23 & 8 &2\\
+130 & 3 & 1 & -\\
+67 & 2 & 1 & - \\
+207 & 2 & 2 & -\\
+74 & 4.5 & 3 & -\\
+47 & 4.42 & 3& -\\
+157 & 3 & 2 & -\\
+136 & 3 & 2 & -\\
+78 & 4 & 1 & -\\
+167 & 2 &1 & -
+\end{tabular}
+\caption{Table shows how many friends and which score user had who may have spread the
+  application, and how many of their friends started to use the
+  application. If a user was a connector to another network, it is
+  calculated to how many new persons the application (appl.) was
+  probably spread.}
+\end{table}
+
+ \begin{center}
+ \begin{table}
+ \label{tab:nospread}
+ \begin{tabular}{ c c c}
+Friends & Score  \\
+\hline
+90 & 1.29 \\
+332 & 3 \\
+233 & 4 \\
+79 & 3 \\
+53 & 1 \\
+89 & 2 \\
+72 & 4 \\
+76 & 1 \\
+264 & 1 \\
+35 & 3 \\
+121 & 4 \\
+289 & 1 \\
+15 & 4 \\
+49 & 4 \\
+0 & 4.75 \\
+80 & 4 \\
+60 & 0 \\
+13 & 2.5 \\
+229 & 0 \\
+53 & 0 \\
+10 & 3 
+\end{tabular}
+\caption{Table shows how many friends and which score user had who did
+  not spread the application.}
+\end{table}
+\end{center}
+
 \end{document}

### 2011-04-15 paper.tex
checked abstract to methodology

@@
 \usepackage{hyperref} %\url can be used, links are highlited
+
+%\usepackage[latin1]{inputenc} % Zeichencodierung
+%\usepackage[T1]{fontenc} % Zeichencodierung
 
@@
 
-\title{Distribution of a Facebook application}
+\title{Spreading of a Facebook Application}
 
@@
 % The outcome was students' perceptions of preparedness.
-This paper investigates, how a small Facebook application 
-distributes among friends. A graph is created which represents users, who
-installed the application, as nodes and friendship between them as
-edges. In addition, metrics are calculated to determine, which
-parameters  make users likely to invite their friends to
-participate.
+Applications on Facebook are popular and attract many
+people. Nevertheless, before installation people must acknowledge that an application
+exists, and they must demand the application, too.
+There may exist several reasons for people to install
+applications, such as intensive usage within their social network, or
+personal interest in a special topic. Persuasion can
+happen virally through Facebook's news stream, by marketing through
+friends, or by directed search on 
+Facebook. Differences in the spreading process are supposed to exist
+for the different kinds of applications.
 
-The application itself is a quiz which asks people 5
-questions, randomly selected from a pool of 20 questions, 
-about dentistry health facts. After the quiz, participants
-get to know if they had a higher score than their friends and who of their
-friends answered the questions they got correctly.
+This paper investigates, how a quiz asking people five randomly
+selected questions about dentistry health facts spreads on
+Facebook. The quiz is made social by providing participants with
+information such as if they were better than their
+friends and other users, and which of their friends could answer the given questions.
 
-Results show users, who yield a high score in the quiz,
-more likely to invent other users than users, who got a worse
-score. In addition, the number of friends did not mark users to be
-relevant for spreading the app. Indeed, people who had less friends
-were much more likely to spread the application.
+Analysis is supported by a tool maintaining an internal representation
+of an extract of Facebook's social graph containing the participants
+as nodes, their friendships as edges, and their basic information
+retrieved from Facebook as well as quiz results as node
+attributes. The tool allows for output of aspects of the internal graph
+in DOT-language, and export of metrics to CSV, too.
+
+Results show that participants, who connect the network of existing
+users to a new one, often achieved a relatively high score in the quiz. New
+participants often had strong connections to the network of people who
+already participated. Indeed, the number of friends did not seem to make
+users more or less likely to gather new participants for the quiz.
 \end{abstract}
@@
 %% or \MSC[2008] code \sep code (2000 is the default)
-Facebook, Social Networking, data mining, social graph
+Facebook, Spreading of Applications, Social Network, data mining, social graph
 \end{keyword}
@@
 become a social network currently used by more than 600 million people
-all over the world\cite{facebook500}. Since 2007, Facebook provides an API allowing
-third party developers to embed their own applications into
+all over the world\cite{facebook500}. Since 2007, Facebook provides an API permitting
+third party developers to embed their own applications in
 Facebook\footnote{http://developers.facebook.com/blog/archive}.
 Subsequent to the F8 conference in April, 2010, Facebook simplified
-access to its social graph via Open Graph Protocol \cite{facebookStats} and allowed
-for integration of external websites. Until October, 2009,
-over 350 000 apps had been seen on Facebook \cite{facebookBlog}.
-Due to current statistics, people install about 20 million apps per day. In addition, ten thousand new
-websites integrate with Facebook every day. \cite{facebookStats}
+access to its social graph by allowing
+external websites for integration in their social graph through Open
+Graph Protocol\cite{facebookStats} .
 
 Due to integration in Facebook's social graph, third party
-applications spare user authentication procedures and can access
-private user information as well. These information can include basic
-information and friend lists, but also interests and further data
-specified by an access token  \footnote{http://developers.facebook.com/docs/authentication/}.
-As the data provided by Facebook, and collected by analyzing user
-behaviour on an application, represent a lot of social information, it
-seems obvious, that these data also allow for studying social groups.
+applications not only spare user authentication procedures, but can also access
+extracts of Facebook's social graph, too. These information provided
+by Facebook detail a user's friend list, basic information, and
+further data to which access has to be granted by access tokens
+\footnote{http://developers.facebook.com/docs/authentication/}. Thus,
+applications let Facebook's social graph enlarge and make people
+spend more time of Facebook. In addition, application developers
+can spread their application virally through appearance in news
+streams, and collect useful information about the social network of
+their users, too.
 
-This paper investigates the distribution process of a quiz on Facebook
-by analysing which parameters make users likely to distribute the application
-and which parameters do not.
+Statistics show development of Facebook applications being very
+attractive nowadays. Until October, 2009, 
+over 350 000 apps had been seen on Facebook \cite{facebookBlog}.
+According to current statistics, about 20 million applications are
+installed per day, and ten thousand new websites integrate with
+Facebook every day, too. \cite{facebookStats}
 
-In the first section, background information
-about how applications can be integrated with Facebook are
-given. Then, the methodology is described in section \ref{sec:method},
-including the quiz, as well as the 
-proceedings used for data collection and evaluation. In section
-\ref{sec:results}, the results are detailed, and in section
-\ref{sec:discussion} and \ref{sec:outlook}, they are discussed and an
-outlook is given for further research.
+This paper investigates the process of spreading of applications on
+Facebook by focusing on the show case of a quiz asking users five randomly
+selected questions about dentistry health facts. User data are
+collected in a MySQL database, and evaluation of the data is
+accomplished by the outputs of a tool maintaining an internal representation of the extract of Facebook's
+social graph the application is allowed to access.
 
-\section{Background}
+The tool allows for output of graphs in \ac{dot} language and output of
+metrics as \ac{csv}. The graphs the tool can output detail how the application
+spreads, and allows for labelling of people (nodes) which connect the
+network of existing user to new networks. The metrics detail with how
+many people users who participated are friends, which score they had,
+and to how many new people they could have spread the application.
+
+In the first section, basic information about Facebook's social graph,
+and integration of applications is
+given. In the next section, the methodology is described by detailing
+the quiz and its building, as well as the tool for data evaluation. Section
+\ref{sec:results} presents the results, and in section
+\ref{sec:discussion} and \ref{sec:outlook}, a discussed follows. Section
+\ref{sec:conclusion} concludes the paper by summing up the results,
+and giving an outlook for further research, too.
+
+\section{Foundations}
 \label{sec:background}
-This section describes the social graph concept, how applications can be integrated with
-Facebook, how authentication and authorisation is done, and in which
-format data from the social graph can be obtained.
+This section details concepts from Facebook, basics about the
+\ac{DOT} language, and at least, it defines the metrics the tool
+explained in section \ref{sec:methodology} can output. Facebook's
+social graph concept is explained in 
+section \ref{sec:social-graph}, section \ref{sec:integr-appl-with}
+describes how applications can be integrated with Facebook, and
+section \ref{sec:auth-auth} makes clear how applications can be
+integrated with Facebook.
 
@@
 \label{sec:social-graph}
-The \textit{social graph} is at Facebook's core. It represents
-connections between people and things they care about
-\cite{facebookDev}. In April, 2010, Facebook included access to the
-social graph via the Open Graph Protocol, which advanced integration of
-external websites into the social graph \cite{facebookDev2}. These websites can make use of
-social plugins such as \textit{Like Buttons} or \textit{Comment Boxes} \cite{facebookDev2}
-and for this reason, the social graph contains not only connections between
-people on Facebook (friend relations), but also between 
-entities such as applications, movie entries on external websites,
-news articles, and much more. As this allows
-people to identify friends on external websites and receive
-information about their friends' attitude towards anything their
-friends have visited and commented before, one can say
-that Facebook's social graph makes the Internet social.
+Facebook's \textit{social graph} can be regarded as its core. It
+represents connections between people and things people care about 
+\cite{facebookDev}. Since April, 2010, Facebook allows for access to its
+social graph via the Open Graph Protocol\footnote{http://ogp.me/}, thus facilitating
+external websites and third party applications to integrate in the social graph by becoming
+additional nodes\cite{facebookDev2}. These additional nodes can for
+instance represent entities such as movies, news articles,
+applications, and much more. People on Facebook can add connections
+from their user node to these additional nodes by clicking on plugins
+provided by Facebook such as \textit{Like Buttons} or entering content in \textit{Comment
+  Boxes}.  \cite{facebookDev2} As images of friends who liked an
+entity, and comments of friends can be shown on external websites via
+iframes, aspects from a user's social network are brought to these
+websites, and for this reason, Facebook is said to make the Internet social.
+
+In general, additional nodes representing external websites are integrated
+unidirectional. Thus, Facebook retrieves the information in which
+entities users were interested in, while the external websites do not
+gain access to Facebook's social graph. Instead, the social
+information is included through iframes.
+In order to integrate nodes bi-directional, the user must permit the
+access, and both, the user, and the entity, which wants to gain access
+to the social graph, must be authenticated. This process is detailed in
+section \ref{sec:auth-auth}. This happens in case of applications on
+Facebook, thus they are included bi-directional and can grab
+information from Facebook's social graph.
 
 The Graph API is one of Facebook's core concepts and presents a consistent
-view of the social graph. Every object has an unique ID and its
-properties can be accessed by requesting the appropriate URL:
+view of the social graph. Every object has an unique ID and if it is
+public, its properties can be accessed by requesting the appropriate URL:
 \url{https://graph.facebook.com/ID}. Listing \ref{list:kbecker} shows
@@
 authorized and authenticated to do so. How this can be achieved is
-discussed in section \ref{sec:auth-auth}. If one tries to access
-non-public information such as the author's list of friends, an error
-in terms of a missing access token is returned. An example is given in
-listing \ref{list:kbeckerfriends}.
+explained in section \ref{sec:auth-auth}. When trying to access
+non-public information without the needed access token, an error
+is returned. Listing \ref{list:kbeckerfriends} gives an example for this.
 
@@
 addition, Facebook grants observation of its own development process by
-making its raodmap public, and by showing its buglist. In addition, a
+making its raodmap public, and by showcasting its buglist. In addition, a
 testserver exists to help developers to analyze if their application
@@
 
+\subsection{Software Metrics}
+\label{sec:metrics}
+Metrics define a mapping of a `particular measurable entity to a
+numerical value' \cite{Lanz06a}. Thus, they allow for analysis and summarization
+of properties which are oftentimes not measurable. In addition, they
+facilitate detection of `outliers in large amounts of data'
+\cite{Lanz06a}. Metrics can be plotted as diagrams or charts, or they
+can be used for visualizations such as graphs connecting nodes
+characterized by metrics. Since humans are trained in understanding signs and
+pictures, visualizations supports understanding and identifying of
+`hidden aspects'. \cite{Lanz06a} In this paper, they are
+employed to characterize users of the quiz. Some metrics can be output
+as \ac{pdf}, and others are used to create the graphs in \ac{dot} language.
+
+The following metrics can be calculated:
+
+\begin{itemize}
+\item A user's number of friends.
+\item A user's score.
+\item The number of friends who also participated in the quiz.
+\item The number of friends who used the application, and belong to a
+new network, thus the only connector between the new users' nodes and
+the other nodes of the graph is the node of the user analyzed.
+\end{itemize}
+
 \section{Methodology}
 \label{sec:method}
-In this section, the quiz is described as well as its
-implementation. Then, it is explained how data are collected for
+This section describes the methodology. At first, the quiz which is
+used to collect data from Facebook's social graph is described as well
+as its implementation (section \ref{sec:quiz}).
+Then, it is explained how data are collected for
 further analysis and how they can be evaluated.
 
-\subsection{The Quiz}
+\subsection{The Analyzed Application}
 \label{sec:quiz}
-The quiz contains questions in German about dentistry health facts. Participants are asked 5
-questions taken from a pool of 20 questions. Each question has 4
-possible answers. Multiple selection is possible, but at least one
-answer is correct. A question is answered correctly, if each correct
-and no incorrect answer have been selected. Figure \ref{fig:quiz}
-shows how the quiz looks like.
+The application analyzed in this paper is a quiz. It is described in
+\ref{sec:aboutQuiz}, and in \ref{sec:implmentation} its implementation
+is detailed.
 
-\begin{figure}
-  \includegraphics[height=3in]{../img/fbquiz.png}
- \caption{The quiz.}
-\label{fig:quiz}
-\end{figure}
+\subsubsection{About The Quiz}
+\label{sec:aboutQuiz}
+The quiz is about dental health fact and also challenging. It can be
+found at the URL \url{http://apps.facebook.com/zahniquiz}.
+Each participants is asked five questions randomly selected
+from a set of twenty questions. A question has four answers, of
+which either one, two, three or each answer can be correct, thus
+the kind of answers refers to the term \textit{multiple selection}.
+A question is scored to be answered correctly, if the correct subset
+was selected by the user, thus each correct and no incorrect answer
+were selected. Each question answered correctly scores one, thus the
+highest score is five. Figure \ref{fig:quiz} gives a screenshot of the quiz.
 
-The quiz is competitive. After the quiz is completed, user are told
-how good they were in comparison to other participants and to their
+The quiz is competitive. After the quiz is completed, users are told
+their score, and in addition, they acknowledge how good they were in
+comparison to other participants as well as to their 
 friends. As shown in figure \ref{fig:solution}, for each question the
 correct solution is given. A user can also invite friends to
-participate by clicking on the appropriate image. This is demonstrated in
-figure \ref{fig:invite}.
+participate. For this issue, profile pictures of a user's friends are
+printed beyond the quiz. By clicking on such an image, an invitation
+can be sent to the friend's Facebook profile.
 
-\subsection{Implementation}
+\subsubsection{Implementation}
 \label{sec:implementation}
-The quiz-application detailed in the last section makes use of
-Facebook's php-\ac{sdk} and JavaScript-\ac{sdk}. It requires
-permissions for \textit{user$\_$birthday} and
+The studied application makes use of 
+Facebook's php-\ac{sdk} and JavaScript-\ac{sdk}\footnote{http://developers.facebook.com/docs/}. It requires
+permissions (see \ref{sec:auth-auth}) for \textit{user$\_$birthday} and
 \textit{publish$\_$stream}.
-Data used by the quiz are stored in a MySQL-database, and php scripts
-handle the application flow. \textit{index.php} maintains calls of
-scripts printing the quiz (\textit{quiz.php}, \textit{question.php}), and displaying
-the correct solution as well as the opportunity to invite friends
-after completion of the quiz
-(\textit{quizResult.php}). \textit{library.php} contains all the
-functions needed.
+The questions and answers of the quiz are stored in a MySQL-database. PHP scripts
+handle the creation of the quiz and
+the Pear DB module \footnote{http://pear.php.net/} is used
+for database queries.
 
-\subsubsection{Database schema}
+The structure of the Facebook application is related to a
+Model-view-controller architecture. \textit{Pear::DB} represents the
+model, files stored in folder \textit{templates} act as view
+(\textit{quizQuestion.php}, \textit{quiz.php},
+\textit{quizResult.php}), and \textit{index.php} assumes the role of
+the controller. \textit{library.php} contains a collection of
+functions used by the various PHP scripts. \textit{facebook.php} and
+scripts from \textit{facebook-sdk} folder are downloaded from
+\url{https://github.com/facebook/php-sdk/} provide the functionality
+of Facebook's PHP \ac{sdk}.
+
+The view operates as follows: \textit{quiz.php} checks if the user
+completed the quiz. If not, it prints the form, loads the styles and
+includes \textit{quizQuestion.php} to print the questions. Otherwise, it
+creates the page shown after the quiz is completed by printing a
+statement commenting the user's score, and by providing users with 
+the following options: Users can print their result into their news
+stream and they can send invitations to their friends' Facebook
+profiles. For both options, Facebook's JavaScript \ac{sdk} is
+used. \textit{quizResult.php} contains the code to  
+print the correct solution after the quiz is completed and is included
+by \textit{quizQuestion.php}.
+
+\paragraph{Database schema}
 \label{sec:database-schema}
@@
 
-\subsubsection{Application flow}
+\paragraph{Application flow}
 \label{sec:application-flow}
-When a user enters, the \textit{OAuth Dialog} is started. Then, the user data
-including gender, birthday, name, Facebook-ID are stored together with
-a timestamp, and column \textit{has-used-app} is set to 1. In
-addition, each user's friends are also stored and column
-\textit{has-used-app} is set to 0. Then, friendships are stored in the
-table \textit{friends}. Next, the quiz is created by randomly choosing
-five questions from the questions table and requiring the answers. To
-make the questions more attractive, the name of an image convenient to
-the questions topic is also stored in the questions table, and this
-image is placed on the left side of each question. Since multiple
-selection is possible, before the answers, which are also queried from
-the MySQL database, checkboxes are placed before each answer.
+When a user accesses the canvas page of the quiz, 
+the \textit{OAuth Dialog} is started automatically by the
+\textit{controller}. If authorization and authentication are completed
+successfully, the user's basic data as well as the birthday are stored together with
+a timestamp in the \textit{User} table. Column \textit{has-used-app} is set to 1. In
+addition, each user's friends list is also stored in \textup{User} and
+\textit{Friends} table, and for these \textit{users}, columns
+\textit{has-used-app} is set to 0.
 
-As soon as a user completed the quiz, evaluation starts by checking
-which questions were answered correctly and by computing the final
-score. Due to multiple selection, user answers are stored in
-an multidimensional array and compared with another multidimensional
-array containing the correct solution and created from the database.
-The given answers are then stored, and in addition, in another table
-(\textit{correctAnsweredQuestions)}
-it is only stored which questions were correct and incorrect answered.
-Some user join the quiz multiple times, and for this reason, each
-score they had is stored in a score table. The user table is also
-changed by entering or updating the average score, computed from each all the scores stored
-in the score table. Then, by using the Java Script \ac{sdk}, the user
-get the option to post the results onto their Facebook wall.
+% the quiz is created by randomly choosing
+% five questions from the questions table and requiring the answers. To
+% make the questions more attractive, the name of an image convenient to
+% the questions topic is also stored in the questions table, and this
+% image is placed on the left side of each question. Since multiple
+% selection is possible, before the answers, which are also queried from
+% the MySQL database, checkboxes are placed before each answer. 
+Next, the quiz is created as mentioned in section
+\ref{sec:implmenetation}.
+After completion, its is evaluated the final score is computed. As
+each answer ought to be stored and multiple selection of answers is
+possible, user answers have to be stored in  a multidimensional.
 
-In order to make the whole thing challenging, it
-is then computed how high the user's score is compared to the friends
-and to all the other users. 
-In addition, the correct solutions are given, and if a user knew the
-right answer, a green check is placed left to the question. Otherwise,
-a red cross is displayed at the same place. At least, the table with
-the friendships and table \textit{correctAnsweredQuestions} are used
-to identify friends  which answered the question correctly. Images of
-them are placed beyond each question's solution together with the
-information that those friends knew the right solution. 
-In the end, users get the chance to invite friends to the app to
-challenge them. For this reason, each friend's picture is added and
-user can click at them. On click, a pre-defined function from
-Facebook's Java Script \ac{sdk} is called to perform the invitation.
+The given answers are then stored in table \textit{GivenAnswers}. In
+table (\textit{correctAnsweredQuestions)} it is stored which questions
+were correct or incorrect answered. This happens to spare complicated
+evaluations based on the \textit{GivenAnswers} table later on.
+Finally, an average score is computed and stored in the user table.
+
+% In order to make the whole thing challenging, it
+% is then computed how high the user's score is compared to the friends
+% and to all the other users. 
+% In addition, the correct solutions are given, and if a user knew the
+% right answer, a green check is placed left to the question. Otherwise,
+% a red cross is displayed at the same place. At least, the table with
+% the friendships and table \textit{correctAnsweredQuestions} are used
+% to identify friends  which answered the question correctly. Images of
+% them are placed beyond each question's solution together with the
+% information that those friends knew the right solution. 
+% In the end, users get the chance to invite friends to the app to
+% challenge them. For this reason, each friend's picture is added and
+% user can click at them. On click, a pre-defined function from
+% Facebook's Java Script \ac{sdk} is called to perform the invitation.
 
@@
 \label{sec:data-evaluation}
-Data evaluation is performed by using the MySQL tables, and
-PHP. In addition, the dot
-language\footnote{http://www.graphviz.org/Documentation.php} is used
+Data evaluation is performed by using the MySQL database, and
+PHP scripts. In addition, the dot
+language\footnote{http://www.graphviz.org/Documentation.php} is employed
 to create graphs.
@@
 \label{sec:results}
-A total of n=48 users participated in the quiz. 5505 users have been
+A total of n=52 users participated in the quiz. 6311 users have been
 stored in the user table. Thus, on average each user brought on
-average 114.7 \textit{new} people, who could read about the application
-in their news stream. 15
+average 121.4 \textit{new} people, who could read about the application
+in their news stream.
 
@@
 \begin{figure}
-  \includegraphics[width=5.2in]{../img/allUserTree.png}
+  \includegraphics[width=5.2in]{../img/tree2.png}
 \caption{Figure shows all users stored in the database. Users who
@@
 had less than hundred friends, which is less than the mean on
-Facebook, i.e. 130 friends \cite{ref:facebookStats}.
+Facebook, i.e. 130 friends \cite{facebookStats}.
 
@@
 \begin{figure}
-  \includegraphics[width=5in]{../img/spreading.png}
+  \includegraphics[width=5in]{../img/spreading5.png}
 \caption{Figure shows all users stored in the database. Users who
@@
 
-\section{Discussion and Outlook}
+\section{Discussion}
 \label{sec:discussion}
@@
 
-In order to get more reliability towards the processes of distribution
-of applications on Facebook, more applications must be analyzed.
-Future research may consider, how patterns change with respect
-to users' age, and if further characteristics can be identified. In
-case of larger applications, it could be studied, if turning points
-or intervals exist, which - when exceeded - make users significantly
-more likely to join the application.
-
-\section{Conclusion}
+\section{Conclusion and Outlook}
 \label{sec:conclusion}
@@
 making people likely to spread the application.
+
+In order to get more reliability towards the processes of spreading
+of applications on Facebook, more applications must be analyzed.
+Future research may consider, how patterns change with respect
+to users' age, and if further characteristics can be identified. In
+case of larger applications, it could be studied, if turning points
+or intervals exist, which - when exceeded - make users significantly
+more likely to join the application.
 
@@
 \label{sec:addendum}
+
+\begin{figure}
+  \includegraphics[height=3in]{../img/fbquiz.png}
+ \caption{The quiz.}
+\label{fig:quiz}
+\end{figure}
+
 \begin{figure}
@@
 
-\begin{figure}
-  \includegraphics[width=3.5in]{../img/fbinvite.png}
-  \caption{This screenshot shows how friends can be invited.}
-\label{fig:invite}
-\end{figure}
+% \begin{figure}
+%   \includegraphics[width=3.5in]{../img/fbinvite.png}
+%   \caption{This screenshot shows how friends can be invited.}
+% \label{fig:invite}
+% \end{figure}
 

### 2011-04-15 paper.tex
checked abstract to results - metrics

@@
 \label{sec:data-evaluation}
-Data evaluation is performed by using the MySQL database, and
-PHP scripts. In addition, the dot
-language\footnote{http://www.graphviz.org/Documentation.php} is employed
-to create graphs.
-
-The evaluation scripts are maintained by \textit{main.php}. A user
-class represents Facebook's social graph internally. Its properties
-are user's Facebook ID, registration date, average score, a list of
-friends, and a list of IDs to whom the user may have spread the
-application. Friendships are represented by a list of references to corresponding
-user objects, and names of users' can be made anonymous if needed.
-
+For data evaluation, a tool coded in PHP exists. It allows for output
+of metrics as \ac{csv} and graphs in \ac{dot}
+language\footnote{http://www.graphviz.org/Documentation.php}.
+The data evaluated by the tool are taken from
+ database tables the quiz also makes use of.
+
+As mentioned in previous sections, the tool maintains an extract of
+Facebook's social graph internally. This graph contains users' basic
+information, friendships, etc. The internal graph is
+extended by information from the quiz, such as if the user has
+installed the application, and which score a user had. The internal graph
+consists of instances of class \textit{user}, which have references
+among each other representing friendships. The whole set of users is
+maintained by \textit{main.php}, which contains a list of all the user
+instances.
+
+Before the graph is created, user names can be made anonymous and the
+results can be stored in the \textit{user} table to provide
+reusability, too. User names are made anonymous by random selection of
+a name from a list of popular baby names from 2009. The list of names was
+taken from \url{http://www.ssa.gov/cgi-bin/popularnames.cgi}.   
+For each gender, hundred names are stored in an array, and if the
+gender is set, a name of same gender is chosen. Otherwise, the name is
+taken randomly. The name of the person who spread the application
+originally is always set to \textit{Alexandra}.
+
+The tool can make a prognoses, which users spread the quiz. To
+identify such users, the following idea is employed:
 A user is supposed to have spread the app if he/she has
-a friend who used the application and who belongs to a \textit{new}
-network. Such persons are found by recursively checking if an user of
+friends who also used the application and who belong to a \textit{new}
+social network. Figure \ref{fig:newNW} gives an example.
+The implementation is as follows: People who are supposed to have
+spread the quiz are found by recursively checking if an user of 
 the application has friends, who also used the application, and whose friends
@@
 
-User names are made anonymous by substituting their names with a
-random name selected from a list of popular baby names
-from 2009, taken from \url{http://www.ssa.gov/cgi-bin/popularnames.cgi}.   
-For each gender, hundred names are stored in an array, and if the
-gender is set, a name of same gender is chosen. Otherwise, the name is
-taken randomly. The name of the person who spread the application
-originally is always set to \textit{Alexandra}.
-
-Output options are a \ac{csv}-file containing metrics calculated from
-the internal social graph as well as various graphs in dot language, created
-from the internal social graph, too.
+To let the tool output the graphs in \ac{dot} language, a parameter
+has to be given to the tool via HTTP-Get method. The parameters are:
+\verb|spreading|, \verb|tree|, \verb|friendsFilled| and
+\verb|friendsScored|. If type \verb|spreading| is selected, only users
+who participated in the quiz are shown. Users who are supposed to have
+spread the application are red colored. Next to each user, the number
+of friends, and the score the user yielded in the quiz are termed. If
+type \verb|tree| is 
+selected, all the users are shown, and nodes of users who participated
+in the quiz are red colored. If type \verb|friendsFilled| is selected,
+only users who participated in the quiz are considered and the
+background color is set corresponding to the number of friends. A user
+with the highest number of friends has background color black, the
+person with the lowest number of friends has background color
+white. If type \verb|friendsScored| is selected, the graph is created
+analogous to type \verb|friendsFilled|, but the background color is
+computed with respect to the score user had in the quiz averagely.
+
+To let the tool output \ac{csv}, the \verb|csv| parameter has to be
+set to \verb|appUser| or to \verb|noAppUser|. 
+If \verb|appUser| is selected, for each user the following metrics are
+calculated: The number of friends, the number of friends who
+participated in the application, and to how many people a person
+probably spread the application.  If \verb|noAppUser| is selected, it
+is only computed how many friends these user had who participated in
+the quiz. It is returned, how many user had one friend, two friends,
+and so on.
+
+Besides the tool, some data are directly retrieved using database
+queries. These data include the number of people in the user table, and
+the number of people who participated in the application.
+
+% Output options are a \ac{csv}-file containing metrics calculated from
+% the internal social graph as well as various graphs in dot language, created
+% from the internal social graph, too.
 % Properties of
@@
 \label{sec:results}
-A total of n=52 users participated in the quiz. 6311 users have been
-stored in the user table. Thus, on average each user brought on
-average 121.4 \textit{new} people, who could read about the application
-in their news stream.
-
-\subsection{Characteristics}
+A total of n=52 users participated in the quiz and 6311 users have been
+stored in the user table. Data were collected from 15th of February to
+15th of April. This section presents, which
+characteristics these users have based on Facebook's insights and on
+metrics computed with the tool discussed in section
+\ref{sec:data-evaluation}. Then, the graphs detailing the spreading of
+the application are shown.
+
+\subsection{Characteristics Of the Participants}
 \label{sec:characteristics}
-
-The characteristics discussed in this section consider data of users
-that are still registered (n=37).
-
-\subsubsection{Age and gender}
+In this section, characteristics about the users who participated in
+the quiz are given. At first, characteristics retrieved from
+Facebook's
+\textit{Insights}\footnote{http://www.facebook.com/help/?search=insights}
+are described, than, metrics collected from database and by the tool are given.
+
+\subsubsection{Facebook's Insights}
+Facebook Insights `provides Facebook Page owners and Facebook Platform
+developers with metrics around their content.'\cite{facebookInsights}
+These metrics are free and can be found in the \textit{My Apps}
+section on the Facebook Developer Platform.
+Facebook Insights considers for its metrics life time installation of an application
+and events happened in a month. In case of the analyzed application,
+Facebook had 50 Lifetime installed users for the quiz on 15th of April, 2011.
+
+\paragraph{Age and gender}
 \label{sec:age-gender}
-$59 \%$ of the registered user are female, $41 \%$ of the participants
+$60 \%$ of the registered user are female, $40 \%$ of the participants
 are male. Table \ref{tab:agegender} shows classification of the users
-by age and gender. It can be seen, that most users ( 70 \%) were at
-the age of 25-34. Only few ($8.4 \%$) were older, and only 21.4 \%
-were younger.
+by age and gender. It can be obtained, that most users ( 68 \%) were at
+the age of 25-34. Few participants ($8 \%$) were older, and about a
+quarter (24 \%) were younger than 25.
 
@@
 \label{tab:agegender}
-\begin{tabular}{l | c c c c}
-Gender\textbackslash Age  & 13-17 & 18-24 & 25-34 & 45-54 \\
+\begin{tabular}{l | c c c c c}
+Gender\textbackslash Age  & 13-17 & 18-24 & 25-34 & 45-54 & 55+\\
 \hline
-female  & 2.7 \% & 16 \% & 35 \% & 5.4 \% \\
-male & 0 \% & 2.7 \% & 35 \% & 2.7 \% 
+female  & 2 \% & 18 \% & 36 \% & 4 \% & 0 \%\\
+male & 0 \% & 4 \% & 32 \% & 2 \%  & 2 \\
 \end{tabular}
@@
 
-\subsubsection{Demography}
+\paragraph{Demography}
 \label{sec:demographie}
 Table \ref{tab:countries} details the origin of the users and table
-\ref{tab:languages} the languages in which the participants use Facebook.
-As it seems obvious for a quiz in German, most visitors came from Germany.
+\ref{tab:languages} the languages in which the participants chose
+Facebook to occur.
 
@@
 \hline
-Germany  & 32 \\
+Germany  & 44 \\
 United Kingdom & 2 \\
@@
 \hline
-German  & 25 \\
-English (UK) & 7 \\
-English (US) & 4 \\
+German  & 34 \\
+English (US) & 10 \\
+English (UK) & 4 \\
 Greek  & 1 \\
+Italian & 1 \\
 \end{tabular}
@@
 \end{center}
+
+\paragraph{Requests}
+The quiz allows for invitation of friends to participation by sending
+requests. In the time of 18th of March to 8th of April, 4 requests
+were sent, and one was accepted. In the month before, no friend
+requests were accepted or ignored.
+
+\subsubsection{Metrics collected by the tool}
+As detailed in section \ref{sec:data-evaluation}, the tool allows for
+output of metrics as \ac{csv}. Metrics about users who participated in
+the quiz are given in table
+\ref{tab:spread}. Table \ref{tab:nouser}
+describes user who did not participate. Table \ref{tab:scorespread}
+and \ref{tab:nospread} sum up metrics from table \ref{tab:spread}.
+
+Five users participated in the application, but
+
+Two tables also located in the addendum describe to how many
+other participants friendships existed (see table \ref{tab:spread} and
+\ref{tab:nospread}), and to how many people of a
+\textit{new} network the application was (probably) distributed by the
+user. $26$ participants were on average $2.54$ friends with other
+participants and those, who spread the application, seemed to have
+more connections to other people than those who did not.
+The average score of people connected to others was $3.02$. It was
+higher than the average score of people not connected to others ($2.41$).
+People not connected to further participants had fewer friends on average ($106.8$)
+than the connected participants ($138.83$).
+
+Table \ref{tab:nouser} details how many friends who participated in
+the application user had, who did not participate in the
+application. Most times, those people just had one friend, but in eleven
+cases, they had four or five participants in their friends list.
 
@@
 
-Two tables also located in the addendum describe to how many
-other participants friendships existed (see table \ref{tab:spread} and
-\ref{tab:nospread}), and to how many people of a
-\textit{new} network the application was (probably) distributed by the
-user. $26$ participants were on average $2.54$ friends with other
-participants and those, who spread the application, seemed to have
-more connections to other people than those who did not.
-The average score of people connected to others was $3.02$. It was
-higher than the average score of people not connected to others ($2.41$).
-People not connected to further participants had fewer friends on average ($106.8$)
-than the connected participants ($138.83$).
-
-Table \ref{tab:nouser} details how many friends who participated in
-the application user had, who did not participate in the
-application. Most times, those people just had one friend, but in eleven
-cases, they had four or five participants in their friends list.
+% \begin{center}
+% \begin{table}
+% \label{tab:coruser}
+% \begin{tabular}{l | c c c}
+% a & a & a & a \\
+
+% \hline
+% b & b & b & b
+% \end{tabular}
+% \caption{dummy}
+% \end{table}
+% \end{center}
+
+\section{Discussion}
+\label{sec:discussion}
+From the results given in section \ref{sec:results} it can be derived
+that the number of friends did not to play a bigger role in the
+process of the application's distribution. The number of connections
+to other users seems to play a bigger 
+role, as it is indicated by table \ref{tab:spread} and figure
+\ref{fig:spreaders}. In addition, a worse score made people unlikely
+to spread the application, just one person with a score less than 3
+did so. Thus, people with a higher score (on average $3.11$, median $3.32$) are
+supposed to have distributed the application. Indeed, some people who
+had four or five friends who participated in the application did not
+install the application.
+
+\section{Conclusion and Outlook}
+\label{sec:conclusion}
+This research indicates, that the spreading of application follows
+certain patterns. Oftentimes, people say that they don't want to
+make a worse impression on Facebook, and this is also reflected in the
+fact, that only people who yield higher scores in the quiz also
+distributed to their friends. In the environment analyzed, dense
+networks with few participants, i.e. in networks in which people know
+each other, made  further members of their network very likely to join
+the application. Indeed, the number of friends did not play a role in
+making people likely to spread the application.
+
+In order to get more reliability towards the processes of spreading
+of applications on Facebook, more applications must be analyzed.
+Future research may consider, how patterns change with respect
+to users' age, and if further characteristics can be identified. In
+case of larger applications, it could be studied, if turning points
+or intervals exist, which - when exceeded - make users significantly
+more likely to join the application.
+
+\include{acronym} % load acronyms
+%% \section{}
+%% \label{}
+
+%% References
+%%
+%% Following citation commands can be used in the body text:
+%% Usage of \cite is as follows:
+%%   \cite{key}          ==>>  [#]
+%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
+%%   \citet{key}         ==>>  Author [#]
+
+%% References with bibTeX database:
+
+\bibliographystyle{elsarticle-harv}
+\bibliography{literature.bib}
+
+%% Authors are advised to submit their bibtex database files. They are
+%% requested to list a bibtex style file in the manuscript if they do
+%% not want to use model1-num-names.bst.
+
+%% References without bibTeX database:
+
+% \begin{thebibliography}{00}
+
+%% \bibitem must have the following form:
+%%   \bibitem{key}...
+%%
+
+% \bibitem{}
+
+% \end{thebibliography}
+
+\newpage
+\section{Tables and Figures}
+\label{sec:addendum}
+
+\begin{figure}
+  \includegraphics[height=3in]{../img/fbquiz.png}
+ \caption{The quiz.}
+\label{fig:quiz}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=3.5in]{../img/fbsolution.png}
+  \caption{Solution of a question.}
+\label{fig:solution}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[height=3in]{../img/newNW.png}
+ \caption{This figure emphasizes users who connect to new social networks with
+   red border.}
+\label{fig:newNW}
+\end{figure}
+
+% \begin{figure}
+%   \includegraphics[width=3.5in]{../img/fbinvite.png}
+%   \caption{This screenshot shows how friends can be invited.}
+% \label{fig:invite}
+% \end{figure}
+
+\begin{figure}
+  \includegraphics[width=5in]{../img/friendsScored.png}
+\caption{Figure shows all users stored in the database. Users who
+  participated have a red text color.}
+\label{fig:friendsScored}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=5in]{../img/friendsFilled.png}
+\caption{Figure shows all users stored in the database. Users who
+  participated have a red text color.}
+\label{fig:friendsFilled}
+\end{figure}
+
+ \begin{table}
+ \label{tab:spread}
+ \begin{tabular}{ c c c c c}
+Anon. Name&Friends&App-friends&Spread App to&Average Score	\\
+Alexandra & 133& 34& 34 & 4.4625 \\
+Evan & 97& 1& 0 & 3.33333 \\
+Justin & 90& 2& 0 & 1.28571 \\
+Tristan & 332& 2& 0 & 3 \\
+Thomas & 396& 3& 0 & 4 \\
+Jose & 233& 1& 0 & 4 \\
+David & 322& 6& 0 & 1.5 \\
+Gianna & 63& 3& 1 & 4 \\
+Makayla & 79& 1& 0 & 3 \\
+Connor & 102& 3& 0 & 0 \\
+Ethan & 91& 4& 1 & 1 \\
+Isabelle & 53& 1& 0 & 1 \\
+Gavin & 89& 1& 0 & 2 \\
+Caleb & 128& 3& 0 & 4 \\
+Sarah & 151& 5& 3 & 3 \\
+Emma & 72& 1& 0 & 4 \\
+Gabrielle & 135& 4& 2 & 3.63636 \\
+David & 254& 3& 2 & 4 \\
+Emily & 220& 5& 0 & 3 \\
+Victoria & 63& 2& 0 & 2 \\
+Brian & 126& 2& 0 & 4 \\
+Jose & 127& 3& 0 & 3 \\
+Thomas & 186& 4& 0 & 4 \\
+Evelyn & 42& 5& 0 & 3 \\
+Paige & 76& 2& 0 & 1 \\
+Hannah & 264& 2& 0 & 1 \\
+Charlotte & 445& 5& 0 & 3 \\
+Elizabeth & 35& 1& 0 & 3 \\
+Carson & 153& 3& 1 & 3 \\
+Carson & 20& 2& 1 & 3 \\
+Nathan & 121& 1& 0 & 4 \\
+Eli & 11& 9& 2 & 4.23077 \\
+Isaac & 290& 1& 0 & 1 \\
+Alexandra & 130& 1& 0 & 3 \\
+Gabriel & 67& 1& 0 & 2 \\
+Paige & 16& 1& 0 & 4 \\
+David & 50& 1& 0 & 4 \\
+Julian & 207& 2& 0 & 2 \\
+Carlos & 3& 3& 0 & 4.75 \\
+Evan & 74& 3& 0 & 4.5 \\
+Sebastian & 47& 3& 0 & 4.41667 \\
+Xavier & 80& 0& 0 & 4 \\
+Evan & 157& 2& 0 & 3 \\
+Brody & 136& 2& 0 & 3 \\
+Luis & 60& 1& 0 & \\
+Allison & 13& 0& 0 & 2.5 \\
+Tyler & 229& 0& 0 & \\
+Emily & 53& 0& 0 & \\
+Khloe & 78& 1& 0 & 4 \\
+Katelyn & 167& 1& 0 & 2 \\
+Kaitlyn & 10& 1& 0 & 3 \\
+Eva & 272& 0& 0 & 4
+\end{tabular}
+\caption{Table details metrics about users who participated in the
+  application. Friends detail the number of friends a user had,
+  App-friends is the number of friends who also participated in the
+  quiz, Spread App To details to how many people a user probably
+  spread the application, and Average Score details to the score the
+  user averagely had in the quiz. The names were made anonymous.}
+\end{table}
+
+ \begin{center}
+ \begin{table}
+ \label{tab:nospread}
+ \begin{tabular}{ c c}
+Number of app friends & Occurrences \\
+\hline
+0 app friends & 5 \\
+1 app friend & 17 \\
+2 app friends & 10 \\
+3 app friends & 10 \\
+4 app friends & 3 \\
+5 app friends & 3\\
+6 app friends & 2\\
+9 app friends & 1\\
+34 app friends & 1 \\
+\end{tabular}
+\caption{Table sums up metrics from table \ref{tab: spread}. It
+  details how many users had 0 friends who also participated in the
+  application, one friend, and so further.}
+\end{table}
+\end{center}
+
+\begin{table}
+\label{tab:scorespread}
+\begin{tabular}{c c}
+Spread to & Average score \\
+1&	2.75 \\
+2&	3.96 \\
+3&	3 \\
+\end{tabular}
+\caption{Table details the average score of people who spread the
+  application to one, two, or three users.}
+\end{table}
 
@@
 
-% \begin{center}
-% \begin{table}
-% \label{tab:coruser}
-% \begin{tabular}{l | c c c}
-% a & a & a & a \\
-
-% \hline
-% b & b & b & b
-% \end{tabular}
-% \caption{dummy}
-% \end{table}
-% \end{center}
-
-\section{Discussion}
-\label{sec:discussion}
-From the results given in section \ref{sec:results} it can be derived
-that the number of friends did not to play a bigger role in the
-process of the application's distribution. The number of connections
-to other users seems to play a bigger 
-role, as it is indicated by table \ref{tab:spread} and figure
-\ref{fig:spreaders}. In addition, a worse score made people unlikely
-to spread the application, just one person with a score less than 3
-did so. Thus, people with a higher score (on average $3.11$, median $3.32$) are
-supposed to have distributed the application. Indeed, some people who
-had four or five friends who participated in the application did not
-install the application.
-
-\section{Conclusion and Outlook}
-\label{sec:conclusion}
-This research indicates, that the spreading of application follows
-certain patterns. Oftentimes, people say that they don't want to
-make a worse impression on Facebook, and this is also reflected in the
-fact, that only people who yield higher scores in the quiz also
-distributed to their friends. In the environment analyzed, dense
-networks with few participants, i.e. in networks in which people know
-each other, made  further members of their network very likely to join
-the application. Indeed, the number of friends did not play a role in
-making people likely to spread the application.
-
-In order to get more reliability towards the processes of spreading
-of applications on Facebook, more applications must be analyzed.
-Future research may consider, how patterns change with respect
-to users' age, and if further characteristics can be identified. In
-case of larger applications, it could be studied, if turning points
-or intervals exist, which - when exceeded - make users significantly
-more likely to join the application.
-
-\include{acronym} % load acronyms
-%% \section{}
-%% \label{}
-
-%% References
-%%
-%% Following citation commands can be used in the body text:
-%% Usage of \cite is as follows:
-%%   \cite{key}          ==>>  [#]
-%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
-%%   \citet{key}         ==>>  Author [#]
-
-%% References with bibTeX database:
-
-\bibliographystyle{elsarticle-harv}
-\bibliography{literature.bib}
-
-%% Authors are advised to submit their bibtex database files. They are
-%% requested to list a bibtex style file in the manuscript if they do
-%% not want to use model1-num-names.bst.
-
-%% References without bibTeX database:
-
-% \begin{thebibliography}{00}
-
-%% \bibitem must have the following form:
-%%   \bibitem{key}...
-%%
-
-% \bibitem{}
-
-% \end{thebibliography}
-
-\newpage
-\section{Addendum}
-\label{sec:addendum}
-
-\begin{figure}
-  \includegraphics[height=3in]{../img/fbquiz.png}
- \caption{The quiz.}
-\label{fig:quiz}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=3.5in]{../img/fbsolution.png}
-  \caption{Solution of a question.}
-\label{fig:solution}
-\end{figure}
-
-% \begin{figure}
-%   \includegraphics[width=3.5in]{../img/fbinvite.png}
-%   \caption{This screenshot shows how friends can be invited.}
-% \label{fig:invite}
-% \end{figure}
-
-\begin{figure}
-  \includegraphics[width=5in]{../img/friendsScored.png}
-\caption{Figure shows all users stored in the database. Users who
-  participated have a red text color.}
-\label{fig:friendsScored}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=5in]{../img/friendsFilled.png}
-\caption{Figure shows all users stored in the database. Users who
-  participated have a red text color.}
-\label{fig:friendsFilled}
-\end{figure}
-
- \begin{table}
- \label{tab:spread}
- \begin{tabular}{ c c c c}
-Friends & Score & Friends who also participated & Probably spread appl. to friends\\
-\hline
-97 & 3.33 & 1 &-\\
-322 & 1.5 & 4 & -\\
-63 & 4 & 1 & 1\\
-102 & 0 & 2 & -\\
-91 & 1 & 3 &1\\
-128 & 4 & 2 & -\\
-151 & 3 & 4 &3\\
-135 & 3.64 & 3 &2\\
-254 & 4 & 2 & 2\\
-220 & 3 & 4 & -\\
-127 & 3 & 2 & -\\
-186 & 4 & 3 & -\\
-42 & 3 & 4 & - \\
-445 & 3 & 4 & - \\
-153 & 3 & 2 &1\\
-20 & 3 & 1 &1\\
-11 & 4.23 & 8 &2\\
-130 & 3 & 1 & -\\
-67 & 2 & 1 & - \\
-207 & 2 & 2 & -\\
-74 & 4.5 & 3 & -\\
-47 & 4.42 & 3& -\\
-157 & 3 & 2 & -\\
-136 & 3 & 2 & -\\
-78 & 4 & 1 & -\\
-167 & 2 &1 & -
-\end{tabular}
-\caption{Table shows how many friends and which score user had who may have spread the
-  application, and how many of their friends started to use the
-  application. If a user was a connector to another network, it is
-  calculated to how many new persons the application (appl.) was
-  probably spread.}
-\end{table}
-
- \begin{center}
- \begin{table}
- \label{tab:nospread}
- \begin{tabular}{ c c c}
-Friends & Score  \\
-\hline
-90 & 1.29 \\
-332 & 3 \\
-233 & 4 \\
-79 & 3 \\
-53 & 1 \\
-89 & 2 \\
-72 & 4 \\
-76 & 1 \\
-264 & 1 \\
-35 & 3 \\
-121 & 4 \\
-289 & 1 \\
-15 & 4 \\
-49 & 4 \\
-0 & 4.75 \\
-80 & 4 \\
-60 & 0 \\
-13 & 2.5 \\
-229 & 0 \\
-53 & 0 \\
-10 & 3 
-\end{tabular}
-\caption{Table shows how many friends and which score user had who did
-  not spread the application.}
-\end{table}
-\end{center}
-
 \end{document}

### 2011-04-15 paper.tex
checked abstract to results - metrics

@@
 
+\subsection{Start of the spreading process}
+\label{sec:start-spre-proc}
+The spreading process was started by the author who posted in the news
+stream a German analogon to `please check out my new app!'. In
+addition, a message on Facebook was sent to 17 friends asking them to
+participate.
+
 \section{Results}
@@
 \subsubsection{Metrics collected by the tool}
+\label{sec:tool-metrics}
 As detailed in section \ref{sec:data-evaluation}, the tool allows for
@@
 
-Five users participated in the application, but
-
-Two tables also located in the addendum describe to how many
-other participants friendships existed (see table \ref{tab:spread} and
-\ref{tab:nospread}), and to how many people of a
-\textit{new} network the application was (probably) distributed by the
-user. $26$ participants were on average $2.54$ friends with other
-participants and those, who spread the application, seemed to have
-more connections to other people than those who did not.
-The average score of people connected to others was $3.02$. It was
-higher than the average score of people not connected to others ($2.41$).
-People not connected to further participants had fewer friends on average ($106.8$)
-than the connected participants ($138.83$).
-
-Table \ref{tab:nouser} details how many friends who participated in
-the application user had, who did not participate in the
-application. Most times, those people just had one friend, but in eleven
-cases, they had four or five participants in their friends list.
-
-\subsection{Spreading of the quiz}
+From the tables it can be derived that 34 users belonged to the
+network of the author who started to spread the application. Thus, 18
+application users came from other networks. 5 user did not have any
+friends who also participated. On average, people except the author
+and who had at least one \textit{app friend} had on average $2.5$ friends who also
+used the application. People who probably spread the application to
+one person had on average $3$ friends who used the quiz, too. People
+who probably spread to two persons had on average $5.33$ friends who
+used it, too. As it is shown in table \ref{tab:scorespread},
+the average score of people who probably spread 
+the application was higher for people who spread to more people. 
+% Two tables also located in the addendum describe to how many
+% other participants friendships existed (see table \ref{tab:spread} and
+% \ref{tab:nospread}), and to how many people of a
+% \textit{new} network the application was (probably) distributed by the
+% user. $26$ participants were on average $2.54$ friends with other
+% participants and those, who spread the application, seemed to have
+% more connections to other people than those who did not.
+% The average score of people connected to others was $3.02$. It was
+% higher than the average score of people not connected to others ($2.41$).
+% People not connected to further participants had fewer friends on average ($106.8$)
+% than the connected participants ($138.83$).
+
+Table \ref{tab:nouser} describes friends of participants, who did not
+participate in the quiz. As each friend was stored, these people also
+occur in table \textit{User} and \textit{Friends}. These friends of
+application users may have received friend requests from other users,
+and, they may have read about the application in their friends' news
+stream.
+It can be obtained, that 11 users exist having 4 or five friends who
+use the application. The larger amount of people had fewer friends who
+used the application.
+
+\subsection{User Response}
+\label{sec:user-response}
+As mentioned in section \ref{sec:start-spre-proc}, 17 friends of the author were
+directly invited to participate in the application. Each of them
+installed the application, thus 17 friends of the author installed the
+application for other reasons. The number of installations per day is
+shown in figure \ref{fig:installations}, the data were exported from
+Facebook Insights. A peak of new installations could be
+found after the request to participate was posted in the news stream
+on 3rd of March, 2011. The days after, further installations
+happened. Six of the people who were asked directly to participate,
+were not asked on 3rd of March, but afterwards. 7 people were asked
+before.
+
+\subsection{Graphs detailing the spreading of the quiz}
 \label{sec:distribution-quiz}
 In this section, graphs illustrating how the
-application spread are presented. The original user names collected from Facebook were made anonymous
-before the graphs were printed (see section \ref{sec:data-evaluation}). Friendships are
+application spread are presented. The original user names collected
+from Facebook were made anonymous
+ (see section \ref{sec:data-evaluation}). Friendships are
 represented by directed edges: If user A has user B in the friend list, an
@@
 
-Figure \ref{fig:allUsers} represents each user stored in user
-table as node, and friendships of those who participated in the
-application as directed edges. Names of users who participated in the quiz are distinguished by
-red font color. The main purpose of this figure is to visualize the
-whole setting and to give an imagination of how many \textit{new}
+Figure \ref{fig:allUsers} represents the graph that is created when
+parameter \verb|tree| is set. In this case, each user stored in \textit{User}
+table becomes a node, and friendships stored in table \textit{Friends}
+are represented by directed edges. Names of users who participated in the quiz are distinguished by
+red font color. The main purpose of this graph type is to
+visualization of the whole spreading process.
+The graph gives an imagination of how many 
 people on Facebook could have read about the application in their 
-news stream. In addition, the figure shows few participants, who are
-not connected to the larger network of the 
-person who started to spread the application.
-
-\begin{figure}
-  \includegraphics[width=5.2in]{../img/tree2.png}
-\caption{Figure shows all users stored in the database. Users who
-  participated have a red text color.}
-\label{fig:allUsers}
-\end{figure}
-
-In the following, only user who participated in the quiz are
-considered. In Figure \ref{fig:spreading} nodes of people, who are
-connector between two networks, have a red font color. The number of
-friends and the average score from quiz are also shown. 
-It can be obtained that in three cases, there are several connections (friendships)
-between the people who participated and belong to a new network. For
-instance, several connections exist between users \textit{Evan},
-\textit{Diego}, \textit{Isabelle}, \textit{Chase}, and \textit{Gebrielle}.
-\textit{Nicholas} and \textit{Chase}, who are friends with those
-people mentioned above, also are friends with \textit{Ethan},
-and \textit{Josiah}.  Then, \textit{Faith} is friend with
-\textit{Owen} and \textit{Colton}, who also know each other, and
-\textit{Mariah} and \textit{Sydney} have \textit{Alexis} as a common
-friend. The figure also shows that most people who spread the
-application had a score greater than or equal to three. At least, it
-can be obtained that half of the people who spread the application
+news stream, or could have been invited by friends to join the
+application. In addition, the graph shows how new networks are
+reached and how dense the connections were in the network of the root
+of the spreading process.
+
+Figure \ref{fig:spreading} shows the graph that can be obtained when
+parameter \verb|spreading| is set. In this case, only users who
+participated in the quiz are considered. It can be obtained, that the
+users Evelyn, Elli, Carlos, Charlotte, David, Sebastian,
+Evan, Thomas, and Gabrielle have several connections among themselves,
+thus they belong probably to a social network. Most people of this
+network had a relatively high score. 
+Further smaller networks exist. One among the users Sarah, two Evans,
+and Brody, and another one among Julian, Khole, David, and Carson. In
+these networks, the application spread to people of a new network. In
+other cases, one new person who had a friend who used the application
+started to use it as well. In
+addition, some further people found the application in the application
+directory on Facebook.
+At least, it can be obtained that half of the people who spread the application
 had less than hundred friends, which is less than the mean on
@@
 
-In the addendum (section \ref{sec:addendum}), two further graphs are
-shown. In figure \ref{fig:friendsScored}, the background color
-represents a user's average score. User with a darker background had a
-higher score with those having a lighter background color. 
-Figure \ref{fig:friendsFilled} visualizes the amount of friends in the
-by giving users having many friends a dark and those having fewer
-friends a lighter background color.
-
-\begin{figure}
-  \includegraphics[width=5in]{../img/spreading5.png}
-\caption{Figure shows all users stored in the database. Users who
-  participated have a red text color.}
-\label{fig:spreading}
-\end{figure}
+% In the addendum (section \ref{sec:addendum}), two further graphs are
+% shown. In figure \ref{fig:friendsScored}, the background color
+% represents a user's average score. User with a darker background had a
+% higher score with those having a lighter background color. 
+% Figure \ref{fig:friendsFilled} visualizes the amount of friends in the
+% by giving users having many friends a dark and those having fewer
+% friends a lighter background color.
 
@@
 \label{sec:discussion}
-From the results given in section \ref{sec:results} it can be derived
-that the number of friends did not to play a bigger role in the
-process of the application's distribution. The number of connections
-to other users seems to play a bigger 
-role, as it is indicated by table \ref{tab:spread} and figure
-\ref{fig:spreaders}. In addition, a worse score made people unlikely
+From the results given in section \ref{sec:results} it can be followed
+that mainly people belonging to the author's social network
+participated in the application. Many of them came after the
+application was solicited on Facebook's news stream, but in the days
+after, further but smaller numbers of installations happened. As participation of friends was posted
+in the news streams of the participants, friends could read about the
+quiz few times. This may have made people curious about the application.
+As it can be obtained in the graphs and in the
+metrics, some users did not have friends who participated. Thus, they
+came for another reason, may be due to interest in dentistry.
+
+Most people who participated were in the age of twenty five to thirty
+four. One reason may be that most of the author's friends are of that
+age. As teenagers have less teeth affected with
+caries than people older than twenty \cite{zahngesundheit}, the chosen
+topic of the question can have increased the effect that mainly people
+in the twenties and thirties participated.
+
+From the metrics it can be concluded that the number of friends did
+not to play a bigger role in the 
+process of the application's spreading. The number of connections
+to other users and the quiz score seemed to play a bigger 
+role, as it is mentioned in section \ref{sec:tool-metrics}. 
+In addition, a worse score made people unlikely
 to spread the application, just one person with a score less than 3
@@
 \label{sec:conclusion}
-This research indicates, that the spreading of application follows
-certain patterns. Oftentimes, people say that they don't want to
+This research indicates, that their is not just one default pattern
+after which applications spread on Facebook. Instead, several facts
+seem to influence this effect. On the one hand, the topic of an
+application and an applications type hit the interest of specific
+people. Furthermore, there are often
+
+. Oftentimes, people say that they don't want to
 make a worse impression on Facebook, and this is also reflected in the
@@
 \begin{figure}
-  \includegraphics[height=3in]{../img/newNW.png}
- \caption{This figure emphasizes users who connect to new social networks with
+  \includegraphics[height=1.5in]{../img/newNW.png}
+ \caption{This figure emphasizes user b who connects the existing
+   network of users to a new social networks with
    red border.}
 \label{fig:newNW}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=5.2in]{../img/tree2.png}
+\caption{Figure shows all users stored in the database. Users who
+  participated have a red text color.}
+\label{fig:allUsers}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=5in]{../img/spreading5.png}
+\caption{Figure shows all users stored in the database. Users who
+  participated have a red text color.}
+\label{fig:spreading}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=5in]{../img/installations.png}
+\caption{Figure shows all users stored in the database. Users who
+  participated have a red text color.}
+\label{fig:installations}
 \end{figure}
@@
 Julian & 207& 2& 0 & 2 \\
-Carlos & 3& 3& 0 & 4.75 \\
+Carlos & 3 & 3 & 0 & 4.75 \\
 Evan & 74& 3& 0 & 4.5 \\
@@
 Brody & 136& 2& 0 & 3 \\
-Luis & 60& 1& 0 & \\
+Luis & 60& 1& 0 & 0\\
 Allison & 13& 0& 0 & 2.5 \\
-Tyler & 229& 0& 0 & \\
-Emily & 53& 0& 0 & \\
+Tyler & 229& 0& 0 & 0\\
+Emily & 53& 0& 0 & 0\\
 Khloe & 78& 1& 0 & 4 \\
@@
 \begin{tabular}{c c}
-Spread to & Average score \\
-1&	2.75 \\
-2&	3.96 \\
-3&	3 \\
+Spread to & Concerned People & Average score \\ 
+1&	4 & 2.75 \\
+2&	3&3.96 \\
+3&	1&3 \\
 \end{tabular}
 \caption{Table details the average score of people who spread the
-  application to one, two, or three users.}
+  application to one, two, or three users, as well as the number of
+  concerned people.}
 \end{table}

### 2011-04-15 paper.tex
abstract updated

@@
 
-\cortext[cor1]{Corresponding author}
-\cortext[cor2]{Principal corresponding author}
-\fntext[fn1]{This document is a collaborative effort.}
+%\cortext[cor1]{Corresponding author}
+%\cortext[cor2]{Principal corresponding author}
+%\fntext[fn1]{This document is a collaborative effort.}
 %\fntext[fn2]{Another author footnote, but a little more longer.}
@@
 %xany number of author footnotes.}
-\tnotetext[tn1]{This is a specimen title.}
+%\tnotetext[tn1]{This is a specimen title.}
 
@@
 There may exist several reasons for people to install
-applications, such as intensive usage within their social network, or
+applications, such as intensive usage within their social network or
 personal interest in a special topic. Persuasion can
-happen virally through Facebook's news stream, by marketing through
+happen virally by Facebook's news stream, by marketing through
 friends, or by directed search on 
@@
 
-This paper investigates, how a quiz asking people five randomly
-selected questions about dentistry health facts spreads on
-Facebook. The quiz is made social by providing participants with
-information such as if they were better than their
-friends and other users, and which of their friends could answer the given questions.
+This paper investigates how a quiz, asking people five randomly
+selected questions about dentistry health facts, spreads on
+Facebook. The quiz is endowed with a social component: After
+completion participants get more than the solution solely. Instead,
+users can see images of friends who could answer the questions they got correctly
+underneath the solution. In addition, they are told how good their
+score was in comparison to their friends.
 
@@
 
-Results show that participants, who connect the network of existing
-users to a new one, often achieved a relatively high score in the quiz. New
+Results show that participants who connect the network of existing
+users to a new one often achieved a relatively high score in the quiz. New
 participants often had strong connections to the network of people who
@@
 \label{tab:scorespread}
-\begin{tabular}{c c}
+\begin{tabular}{c c c}
 Spread to & Concerned People & Average score \\ 

### 2011-04-15 paper.tex
changes up to 4.2

@@
 participants often had strong connections to the network of people who
-already participated. Indeed, the number of friends did not seem to make
+already participated. Indeed\annSBW{passt da mal überhaupt nicht}, the number of friends did not seem to make
 users more or less likely to gather new participants for the quiz.
@@
 third party developers to embed their own applications in
-Facebook\footnote{http://developers.facebook.com/blog/archive}.
+Facebook\footnote{http://developers.facebook.com/blog/archive}\annSBW{sowas kannste nicht verlinken ... wieso sind das fussnoten und keine Quellen?}.
 Subsequent to the F8 conference in April, 2010, Facebook simplified
 access to its social graph by allowing
-external websites for integration in their social graph through Open
+external websites for integration\annSBW{falsche grammatik} in their social graph through \annSBW{the} Open
 Graph Protocol\cite{facebookStats} .
@@
 Due to integration in Facebook's social graph, third party
-applications not only spare user authentication procedures, but can also access
+applications not only spare user\annSBW{s from} authentication procedures, but can also access
 extracts of Facebook's social graph, too. These information provided
@@
 \ref{sec:results} presents the results, and in section
-\ref{sec:discussion} and \ref{sec:outlook}, a discussed follows. Section
+\ref{sec:discussion} and \ref{sec:outlook}, a discussed follows \annSBW{wording}. Section
 \ref{sec:conclusion} concludes the paper by summing up the results,
-and giving an outlook for further research, too.
+and giving an outlook for further research, too\annSBW{loose the too}.
 
@@
 describes how applications can be integrated with Facebook, and
-section \ref{sec:auth-auth} makes clear how applications can be
+section \ref{sec:auth-auth} makes clear \annSBW{no it doesn't} how applications can be
 integrated with Facebook.
@@
 addition, Facebook grants observation of its own development process by
-making its raodmap public, and by showcasting its buglist. In addition, a
+making its raodmap \annSBW{typo} public, and by showcasting \annSBW{typo and wrong word (showcasing is positiv)} its buglist. In addition, a
 testserver exists to help developers to analyze if their application
@@
 \ref{sec:method} implements the O-Auth Dialog from the PHP-\ac{sdk},
-this variant will be described in detail. It shall just be mentioned,
+this variant will be described in detail. It shall just be mentioned,\annSBW{ loose the comma}
 that Facebook also allows for manual execution of the steps to receive
@@
 wants to grant the application access to some data specified by the
-application with the scope parameter. One should note, that no
-login data are sent to the application, thus, this is how Facebook
+application with the scope parameter. One should note, that \annSBW{ loose the comma} no
+login data are sent to the application, thus, \annSBW{thus triffts mal garnicht, das komma is zu viel am besten ganzen satz anders} this is how Facebook
 establishes a trust relation. 
@@
 
+\annSBW{HTTPS? Security überlegungen?}
+
 \subsection{Graphs with DOT language}
@@
 The \ac{dot} language allows for plain text description of
-graphs. There are few programs that can process \ac{dot} graphs, most
+graphs. There are few programs that can process \ac{dot} graphs, most \annSBW{ not by a long shot}
 of them are part of the
@@
 numerical value' \cite{Lanz06a}. Thus, they allow for analysis and summarization
-of properties which are oftentimes not measurable. In addition, they
+of properties which are oftentimes not measurable\annSBW{gerad eben haste noch das gegenteil behauptet}. In addition, they
 facilitate detection of `outliers in large amounts of data'
@@
 \label{sec:aboutQuiz}
-The quiz is about dental health fact and also challenging. It can be
+The quiz is about dental health fact and also challenging\annSBW{loose that}. It can be
 found at the URL \url{http://apps.facebook.com/zahniquiz}.
@@
 which either one, two, three or each answer can be correct, thus
-the kind of answers refers to the term \textit{multiple selection}.
+the kind of answers refers to the term \textit{multiple selection} \annSBW{der Satz is ganz im Arsch}.
 A question is scored to be answered correctly, if the correct subset
-was selected by the user, thus each correct and no incorrect answer
+was selected by the user, thus \annSBW{i.E. ... thus should be used seldom if at all} each correct and no incorrect answer
 were selected. Each question answered correctly scores one, thus the
@@
 permissions (see \ref{sec:auth-auth}) for \textit{user$\_$birthday} and
-\textit{publish$\_$stream}.
+\textit{publish$\_$stream} \annSBW{erklären!}.
 The questions and answers of the quiz are stored in a MySQL-database. PHP scripts
@@
 the \textit{OAuth Dialog} is started automatically by the
-\textit{controller}. If authorization and authentication are completed
+\textit{controller} \annSBW{vorhin haste noch gesagt FB macht das}. If authorization and authentication are completed
 successfully, the user's basic data as well as the birthday are stored together with
@@
 After completion, its is evaluated the final score is computed. As
-each answer ought to be stored and multiple selection of answers is
-possible, user answers have to be stored in  a multidimensional.
+each answer ought to be stored and multiple selection of answers is \annSBW{multiple answers are}
+possible, user answers have to be stored in  a multidimensional \annSBW{what?}.
 
@@
 In this section, graphs illustrating how the
-application spread are presented. The original user names collected
+application spread \annSBW{-s/-ed} are presented. The original user names collected
 from Facebook were made anonymous

### 2011-04-16 paper.tex
abstract updated

--- 2011-04-15 paper.tex
@@
 Results show that participants who connect the network of existing
-users to a new one often achieved a relatively high score in the quiz. New
-participants often had strong connections to the network of people who
-already participated. Indeed, the number of friends did not seem to make
-users more or less likely to gather new participants for the quiz.
+users to a new one often achieve a comparatively high score in the
+quiz. In the most cases, new participants have strong relations to the network of people who
+already participated. Indeed, the number of friends does not seem to
+have any effect on whether a user gathers new participants for the quiz.
 \end{abstract}
@@
 \label{sec:introduction}
-Founded in 2004, Facebook\footnote{www.facebook.com} has
+Founded in 2004 Facebook\footnote{www.facebook.com} has
 become a social network currently used by more than 600 million people
-all over the world\cite{facebook500}. Since 2007, Facebook provides an API permitting
-third party developers to embed their own applications in
+all over the world\cite{facebook500}. Since 2007, Facebook provides an API, permitting
+third party developers to embed their own applications into
 Facebook\footnote{http://developers.facebook.com/blog/archive}.
-Subsequent to the F8 conference in April, 2010, Facebook simplified
+Subsequent to the F8 conference in April, 2010, Facebook simplifies
 access to its social graph by allowing
 external websites for integration in their social graph through Open
-Graph Protocol\cite{facebookStats} .
+Graph Protocol.\cite{facebookStats}
 
@@
 applications not only spare user authentication procedures, but can also access
-extracts of Facebook's social graph, too. These information provided
-by Facebook detail a user's friend list, basic information, and
-further data to which access has to be granted by access tokens
+extracts of Facebook's social graph, too. These information detail a
+user's friend list, basic information, and 
+further data. Access to these data has to be granted by access tokens
 \footnote{http://developers.facebook.com/docs/authentication/}. Thus,
 applications let Facebook's social graph enlarge and make people
-spend more time of Facebook. In addition, application developers
-can spread their application virally through appearance in news
-streams, and collect useful information about the social network of
-their users, too.
-
-Statistics show development of Facebook applications being very
-attractive nowadays. Until October, 2009, 
-over 350 000 apps had been seen on Facebook \cite{facebookBlog}.
-According to current statistics, about 20 million applications are
-installed per day, and ten thousand new websites integrate with
-Facebook every day, too. \cite{facebookStats}
-
-This paper investigates the process of spreading of applications on
-Facebook by focusing on the show case of a quiz asking users five randomly
+spend more time on Facebook. In addition, application developers
+can spread their application virally in news
+streams, and thereby they collect useful information about the social network of
+their users.
+
+Statistics show that the development of Facebook applications is becoming more
+and more popular. Until October 2009, 
+over three hundred fifty thousand applications have appeared on Facebook \cite{facebookBlog}.
+According to current statistics about twenty million applications are
+installed every day, and ten thousand new websites integrate with
+Facebook every day. \cite{facebookStats}
+
+This paper investigates the way applications spread on
+Facebook. For this purpose, a quiz was built asking users five randomly
 selected questions about dentistry health facts. User data are
-collected in a MySQL database, and evaluation of the data is
-accomplished by the outputs of a tool maintaining an internal representation of the extract of Facebook's
+collected in a MySQL database. The Evaluation of the data is
+accomplished through the output of a tool which maintains an internal
+representation of the extract of Facebook's 
 social graph the application is allowed to access.
 
-The tool allows for output of graphs in \ac{dot} language and output of
-metrics as \ac{csv}. The graphs the tool can output detail how the application
-spreads, and allows for labelling of people (nodes) which connect the
-network of existing user to new networks. The metrics detail with how
-many people users who participated are friends, which score they had,
-and to how many new people they could have spread the application.
+The tool allows for the output of graphs in \ac{dot} language and the output of
+metrics as \ac{csv}. The graphs the tool puts out detail how the application
+spreads, and allow for labelling of people (nodes) that connect the
+network of existing user to new networks. The metrics detail the
+number of friends users have, the average score,
+and finally, the amount of users gained through the participant.
 
@@
 given. In the next section, the methodology is described by detailing
-the quiz and its building, as well as the tool for data evaluation. Section
+the quiz and its implementation, as well as a tool created for data
+evaluation. Section 
 \ref{sec:results} presents the results, and in section
-\ref{sec:discussion} and \ref{sec:outlook}, a discussed follows. Section
+\ref{sec:discussion}, a discussion follows. Section
 \ref{sec:conclusion} concludes the paper by summing up the results,
-and giving an outlook for further research, too.
+and giving an outlook on further research.
 
@@
 This section details concepts from Facebook, basics about the
-\ac{DOT} language, and at least, it defines the metrics the tool
-explained in section \ref{sec:methodology} can output. Facebook's
+\ac{dot} language, and finally, it defines the metrics the
+data-evaluation tool (see section \ref{sec:methodology}) can put out. Facebook's
 social graph concept is explained in 
@@
 \label{sec:conclusion}
-This research indicates, that their is not just one default pattern
-after which applications spread on Facebook. Instead, several facts
-seem to influence this effect. On the one hand, the topic of an
-application and an applications type hit the interest of specific
-people. Furthermore, there are often
+This research indicates that no default patterns exist describing the 
+spreading of applications on Facebook. Instead, a variety of
+factors seems to contribute to the investigated process. On the one
+hand, the application's topic limits the target group
+automatically.
+
+Beside the 
+applications topic, which limits the target group to people naturally,
+
+seem to influence this effect: On the one hand, the chosen topic of an
+application 
+people. On the other hand, their are factors such as the number of
+
+Furthermore, there
 
@@
 
-\begin{figure}
-  \includegraphics[width=5in]{../img/friendsScored.png}
-\caption{Figure shows all users stored in the database. Users who
-  participated have a red text color.}
-\label{fig:friendsScored}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=5in]{../img/friendsFilled.png}
-\caption{Figure shows all users stored in the database. Users who
-  participated have a red text color.}
-\label{fig:friendsFilled}
-\end{figure}
+% \begin{figure}
+%   \includegraphics[width=5in]{../img/friendsScored.png}
+% \caption{Figure shows all users stored in the database. Users who
+%   participated have a red text color.}
+% \label{fig:friendsScored}
+% \end{figure}
+
+% \begin{figure}
+%   \includegraphics[width=5in]{../img/friendsFilled.png}
+% \caption{Figure shows all users stored in the database. Users who
+%   participated have a red text color.}
+% \label{fig:friendsFilled}
+% \end{figure}
 

### 2011-04-17 paper.tex
version for the course

@@
 Applications on Facebook are popular and attract many
-people. Nevertheless, before installation people must acknowledge that an application
+people. Nevertheless, prior to installation people must acknowledge that an application
 exists, and they must demand the application, too.
@@
 personal interest in a special topic. Persuasion can
-happen virally by Facebook's news stream, by marketing through
-friends, or by directed search on 
+happen virally by Facebook's news stream or by marketing through
+friends, but also through directed search on 
 Facebook. Differences in the spreading process are supposed to exist
@@
 
-This paper investigates how a quiz, asking people five randomly
-selected questions about dentistry health facts, spreads on
-Facebook. The quiz is endowed with a social component: After
-completion participants get more than the solution solely. Instead,
-users can see images of friends who could answer the questions they got correctly
-underneath the solution. In addition, they are told how good their
-score was in comparison to their friends.
-
-Analysis is supported by a tool maintaining an internal representation
-of an extract of Facebook's social graph containing the participants
-as nodes, their friendships as edges, and their basic information
-retrieved from Facebook as well as quiz results as node
-attributes. The tool allows for output of aspects of the internal graph
+This paper investigates how a quiz application spreads on
+Facebook. A methodology is developed to conclude from a graph of
+participants which people were very likely responsible for the application's spreading.
+
+The quiz is about dentistry health facts and asks its participants five randomly
+selected questions. In addition, it is endowed with a social component: After
+completion of the quiz participants do not get the solution solely. Instead,
+beyond the solution images of friends are displayed who knew the right answer of the
+questions the user got. In addition, users are told how good their 
+score was in comparison to their friends and to the whole set of users.
+
+Analysis of the applications way of spreading is supported by a tool maintaining an internal representation
+of an extract of Facebook's social graph. The tool's internal graph
+represents the participants as nodes, their friendships as edges, and their basic information
+retrieved from Facebook as well as quiz results as
+attributes of the nodes. The methodology to identify people who
+contributed to the spreading process was implemented, too. The tool
+allows for output of aspects of the internal graph 
 in DOT-language, and export of metrics to CSV, too.
 
-Results show that participants who connect the network of existing
-users to a new one often achieve a comparatively high score in the
-quiz. In the most cases, new participants have strong relations to the network of people who
+Results show that participants who are supposed to contribute to the
+application's spreading often achieve a comparatively high score in the
+quiz. Particular user's posts in the news stream seem to influence the
+applications growth, while other users post do not show this
+effect. New participants often had strong relations to the network of people who
 already participated. Indeed, the number of friends does not seem to
@@
 \label{sec:introduction}
-Founded in 2004 Facebook\footnote{www.facebook.com} has
+Founded in 2004 Facebook\footnote{www.facebook.com on 14th of April 2011} has
 become a social network currently used by more than 600 million people
@@
 third party developers to embed their own applications into
-Facebook\footnote{http://developers.facebook.com/blog/archive}.
+Facebook.
 Subsequent to the F8 conference in April, 2010, Facebook simplifies
@@
 Due to integration in Facebook's social graph, third party
-applications not only spare user authentication procedures, but can also access
-extracts of Facebook's social graph, too. These information detail a
+applications not only spare user from authentication procedures, but can also access
+extracts of Facebook's social graph, too. This information details a
 user's friend list, basic information, and 
-further data. Access to these data has to be granted by access tokens
-\footnote{http://developers.facebook.com/docs/authentication/}. Thus,
-applications let Facebook's social graph enlarge and make people
+further data. Access to this data has to be granted by access tokens. \cite{facebookDevAuth}
+Thus, applications let Facebook's social graph enlarge and make people 
 spend more time on Facebook. In addition, application developers
@@
 
-This paper investigates the way applications spread on
+This paper investigates the way in which an application spreads on
 Facebook. For this purpose, a quiz was built asking users five randomly
@@
 \ac{dot} language, and finally, it defines the metrics the
-data-evaluation tool (see section \ref{sec:methodology}) can put out. Facebook's
+data-evaluation tool (see section \ref{sec:method}) can put out. Facebook's
 social graph concept is explained in 
@@
 describes how applications can be integrated with Facebook, and
-section \ref{sec:auth-auth} makes clear how applications can be
+section \ref{sec:auth-auth} illustrates the way how applications can be
 integrated with Facebook.
 
-\subsection{Social Graph}
+\subsection{Facebook's Social Graph}
 \label{sec:social-graph}
@@
 represents connections between people and things people care about 
-\cite{facebookDev}. Since April, 2010, Facebook allows for access to its
+\cite{facebookDev}. Since April 2010, Facebook allows access to its
 social graph via the Open Graph Protocol\footnote{http://ogp.me/}, thus facilitating
 external websites and third party applications to integrate in the social graph by becoming
-additional nodes\cite{facebookDev2}. These additional nodes can for
-instance represent entities such as movies, news articles,
-applications, and much more. People on Facebook can add connections
-from their user node to these additional nodes by clicking on plugins
-provided by Facebook such as \textit{Like Buttons} or entering content in \textit{Comment
-  Boxes}.  \cite{facebookDev2} As images of friends who liked an
+additional nodes\cite{facebookDev2}. For instance, these additional
+nodes can represent entities such as movies, news articles, 
+applications, and many more. People on Facebook can add edges
+between their user node to these additional nodes by clicking on plugins
+provided by Facebook, such as \textit{Like Buttons} or entering content in \textit{Comment
+  Boxes}.  \cite{facebookDev2} As images of friends liking an
 entity, and comments of friends can be shown on external websites via
 iframes, aspects from a user's social network are brought to these
-websites, and for this reason, Facebook is said to make the Internet social.
+websites. Therefore, Facebook is said to socialize the Internet.
 
 In general, additional nodes representing external websites are integrated
-unidirectional. Thus, Facebook retrieves the information in which
-entities users were interested in, while the external websites do not
+unidirectionally. Thus, Facebook retrieves the information about the
+entities users were interested in, whereas the external websites do not
 gain access to Facebook's social graph. Instead, the social
-information is included through iframes.
-In order to integrate nodes bi-directional, the user must permit the
-access, and both, the user, and the entity, which wants to gain access
+information is included via iframes.
+In order to integrate nodes bi-directionally, the user must permit 
+access to its data, and both,  user and entity, wanting to gain access
 to the social graph, must be authenticated. This process is detailed in
-section \ref{sec:auth-auth}. This happens in case of applications on
-Facebook, thus they are included bi-directional and can grab
+section \ref{sec:auth-auth} and matters in the case of applications on
+Facebook. Thus, applications are included bi-directional and can grab
 information from Facebook's social graph.
@@
 information, an access token has to be included in the Graph API
-request. To get this token, the accessing entity must be
-authorized and authenticated to do so. How this can be achieved is
+request. To get this token, the accessing entity has to be
+authorized and authenticated to do so. A way to achieve this is
 explained in section \ref{sec:auth-auth}. When trying to access
-non-public information without the needed access token, an error
-is returned. Listing \ref{list:kbeckerfriends} gives an example for this.
+non-public information without the necessary access token, an error
+is returned. Listing \ref{list:kbeckerfriends} gives an example.
 
@@
 Besides the Graph API, Facebook's social graph can also be accessed
-with the REST-API, which is in the processes of deprecating
+by using an older API that facebook refers to as its `REST-API'. This API is in the processes of deprecating
 \cite{facebookDev3}. Both, the Graph API and the REST-API support
@@
 
-\subsection{Integration of Applications with Facebook}
+\subsection{Integration of applications with Facebook}
 \label{sec:integr-appl-with}
-Applications on Facebook are hosted on external severs, and are loaded
+Applications on Facebook are hosted on external severs and are loaded
 into a \textit{Canvas Page} by using iFrames. After registration
@@
 can be found under the URL \url{http://apps.facebook.com/your_app }.
-As soon as the application exists for some month and has
-some users registered, it can be added to Facebook's application
+When the application has existed for some months and 
+some users have registered themselves, it can be added to Facebook's application
 index.
@@
 process. \ac{sdks} exist for popular programming languages and provide
-sets of pre-defined functions for communication with Facebook. For
+sets of pre-defined functions for the purpose of communication with Facebook. For
 instance, they include the O-Auth 2.0 dialog which is described in
 section \ref{sec:auth-auth}. In
-addition, Facebook grants observation of its own development process by
-making its raodmap public, and by showcasting its buglist. In addition, a
-testserver exists to help developers to analyze if their application
+addition, Facebook grants the observation of its own development process by
+making its raodmap public and by publishing its buglist. Furthermore, a
+testserver exists in order to help developers analyze whether their application
 is going to run with planned features from Facebook. 
-Facebook provides an \textit{insights}-feature which makes
-statistics about the applications available. \cite{oreilly}.
-
-\subsection{Authentication and Authorization}
+Facebook provides an \textit{Insights}-feature which makes
+statistics about an application accessible. \cite{oreilly}.
+
+\subsection{Authentication and authorization}
 \label{sec:auth-auth}
@@
 \ref{sec:method} implements the O-Auth Dialog from the PHP-\ac{sdk},
-this variant will be described in detail. It shall just be mentioned,
+this variant will be described in detail. It ought be mentioned,
 that Facebook also allows for manual execution of the steps to receive
-access tokens.\cite{facebookDevAuth}
+access tokens.\cite{facebookDevAuth}  Indeed, this is
+out of scope for the case of this paper.
 
@@
 and authorization as well as authentication of the
-application. If these three steps are completed, the application is
+application. Whenever these three steps are completed, the application is
 issued an \textit{user access token}. If more than basic information
@@
 authentication take place with OAuthDialog. The \textit{app server}
-illustrates the server on which the app is actually
+depicts the server on which the application is actually
 running. \textit{Facebook} represents all the Facebook servers, on
-which perform authentication and authorization. The \textit{OAuth
+which authentication and authorization are performed. The \textit{OAuth
   Dialog} runs on the browser of the client who is going to use the
@@
 
-\begin{figure}
-\label{fig:authorization}
-  \includegraphics[width=4in]{../img/fbinteraction3.png}
-  \caption{Facebook establishes trust relation by not sending login
-    data to app server, but using access tokens instead for
-    data exchange with app server.}
-\end{figure}
-
 When clients access the canvas page of the application, they are
 redirected to the OAuth Dialog (running on a Facebook server) and
-provided with the application's ID. Then, user authentication and
-app authorization is performed, by involving the client and Facebook
+provided with the application's ID. Afterwards, user authentication and
+authorization of the application are performed by involving the client and Facebook
 only. User authentication is done by logging in on Facebook (if necessary) and
-authorization of the application is done by asking the user if he/she
+authorization of the application is done by asking the user whether he/she
 wants to grant the application access to some data specified by the
 application with the scope parameter. One should note, that no
-login data are sent to the application, thus, this is how Facebook
+login data are sent to the application. Thus, this is how Facebook
 establishes a trust relation. 
-If the user authorizes the application, an \textit{authorization code} is returned and
-the user is redirected to the application, to which the
-\textit{authorization code} is forwarded. During registration of the
-application, an \textit{application secret} code was
+If the user authorizes the application, an \textit{authorization code}
+will be returned and
+the user is redirected to the application to which the
+\textit{authorization code} is forwarded. During the registration of the
+application, an \textit{application secret} code is
 created. In order to authenticate the application, the
@@
 The \ac{dot} language allows for plain text description of
-graphs. There are few programs that can process \ac{dot} graphs, most
+graphs. There are few programs that can process \ac{dot} graphs. Many
 of them are part of the
 \textit{Graphviz}\footnote{http://www.graphviz.org}-package. 
-The language allows for directed and undirected graphs, attributes can
-be set and colors as well as different shapes for nodes and edges can
-be used. The basic syntax is very easy, the graph shown in figure
+The language allows for creation of directed and undirected graphs. Attributes such
+colors and shapes for nodes and edges can
+be set. The graph shown in figure
 \ref{fig:dot} has the \ac{dot}-code given in listing \ref{list:dot}.
@@
 
-\begin{figure}
-  \includegraphics[width=0.4in]{../img/ab.png}
-\caption{A very simple graph in \ac{dot}-language.}
-\label{fig:dot}
-\end{figure}
-
+% Figure DOT 1 and 2
 Labels and colors can be added by defining the node in the head of the
@@
 the corresponding graph is given in figure \ref{fig:dot2}.
-
-\begin{figure}
-  \includegraphics[width=0.4in]{../img/graphDot.png}
-\caption{A very simple graph with node a blue boxed and fontcolor set
-  to red.}
-\label{fig:dot2}
-\end{figure}
 
@@
 \label{sec:metrics}
-Metrics define a mapping of a `particular measurable entity to a
+Metrics define a mapping from a `particular measurable entity to a
 numerical value' \cite{Lanz06a}. Thus, they allow for analysis and summarization
-of properties which are oftentimes not measurable. In addition, they
-facilitate detection of `outliers in large amounts of data'
-\cite{Lanz06a}. Metrics can be plotted as diagrams or charts, or they
-can be used for visualizations such as graphs connecting nodes
-characterized by metrics. Since humans are trained in understanding signs and
-pictures, visualizations supports understanding and identifying of
-`hidden aspects'. \cite{Lanz06a} In this paper, they are
-employed to characterize users of the quiz. Some metrics can be output
-as \ac{pdf}, and others are used to create the graphs in \ac{dot} language.
-
-The following metrics can be calculated:
+of properties which oftentimes are not comparable without the metric. In addition, they
+facilitate the detection of `outliers in large amounts of data'
+\cite{Lanz06a}. Metrics can either be plotted as diagrams or charts, or they
+can be used for visualizations. Such are graphs connecting nodes
+characterized by metrics.
+
+Since humans are trained in understanding signs and
+pictures, visualizations support the understanding and identification of
+`hidden aspects'.\cite{Lanz06a} In this paper, they are
+employed to characterize users of the quiz. A tool evaluating the quiz
+from the quiz exists, which can put out metrics
+as \ac{csv}. In addition, it uses metrics are used to create the graphs in \ac{dot} language.
+
+The following metrics can be printed to \ac{csv} files:
 
@@
 \item The number of friends who also participated in the quiz.
-\item The number of friends who used the application, and belong to a
-new network, thus the only connector between the new users' nodes and
-the other nodes of the graph is the node of the user analyzed.
+\item The number of friends who became participants due to
+participation of the person analyzed. These persons are regarded as
+persons who spread the application.
 \end{itemize}
+
+Further metrics are provided by Facebook Insights (see section
+\ref{sec:integr-appl-with}). These include the number of Daily
+App Installations, the Daily Application Usage, Monthly Active Users,
+and the number of users who belong to a specific age group, or to a
+specific gender.
 
@@
 \label{sec:method}
-This section describes the methodology. At first, the quiz which is
-used to collect data from Facebook's social graph is described as well
-as its implementation (section \ref{sec:quiz}).
-Then, it is explained how data are collected for
-further analysis and how they can be evaluated.
-
-\subsection{The Analyzed Application}
-\label{sec:quiz}
-The application analyzed in this paper is a quiz. It is described in
-\ref{sec:aboutQuiz}, and in \ref{sec:implmentation} its implementation
-is detailed.
-
-\subsubsection{About The Quiz}
+In this section, it is detailed how the spreading of an application on
+Facebook can be analyzed. At first, the quiz developed and employed for this issue is
+explained. Afterwards, a method is described how the set of
+participants can be transferred into a graph and how this
+graph can be used to identify users who can have contributed to the applications
+spreading. After this, the implementation of the quiz is detailed. In
+the end of the chapter, it is described how the data were
+evaluated. As a tool was developed for this purpose, a focus is put on
+the way the tool  operates. The section finished with an explanation of
+the way in which the spreading of the application was initialized.
+
+\subsection{The application to be analyzed}
 \label{sec:aboutQuiz}
-The quiz is about dental health fact and also challenging. It can be
+The application to be analyzed is a quiz about dental health fact. It is to be
 found at the URL \url{http://apps.facebook.com/zahniquiz}.
-Each participants is asked five questions randomly selected
-from a set of twenty questions. A question has four answers, of
-which either one, two, three or each answer can be correct, thus
+Each participant is asked five questions selected
+from a set of twenty questions randomly. A question has four answers, of
+which either one, two, three or each answer can be
+correct. Consequently,
 the kind of answers refers to the term \textit{multiple selection}.
-A question is scored to be answered correctly, if the correct subset
-was selected by the user, thus each correct and no incorrect answer
-were selected. Each question answered correctly scores one, thus the
+A question is scored as a right answer, if the fitting subset was
+selected by the user. 
+Each question answered correctly scores one. Hence, the
 highest score is five. Figure \ref{fig:quiz} gives a screenshot of the quiz.
 
-The quiz is competitive. After the quiz is completed, users are told
-their score, and in addition, they acknowledge how good they were in
+The quiz is competitive. After the quiz is completed the score is
+displayed, and in addition, they acknowledge how good they were in 
 comparison to other participants as well as to their 
-friends. As shown in figure \ref{fig:solution}, for each question the
-correct solution is given. A user can also invite friends to
-participate. For this issue, profile pictures of a user's friends are
-printed beyond the quiz. By clicking on such an image, an invitation
-can be sent to the friend's Facebook profile.
-
-\subsubsection{Implementation}
+friends. As shown in figure \ref{fig:solution} for each question the
+correct solution is shown.
+
+To invite friends to the quiz, profile
+pictures of a user's friends are 
+printed beyond the quiz. By clicking on such an image,  requests to
+participate in the applications 
+can be sent to the appropriate friend.
+
+\subsection{User-Graph and identification of people who can have contributed to the application's spreading}
+\label{sec:user-graph-ident}
+To identify characteristics of people who contributed to the spreading
+of the application a graph can be created. In this section, this graph
+will be termed User-Graph.
+
+The nodes of the User-Graph represent either people who actually participated in the
+quiz or friends of these people. Each node has some attributes: The
+user's name, a randomly selected name to make the person anonymous,
+and an id. If a person participated  
+in the quiz, additional attributes are set. They refer to a
+user's birthday, the gender, and information about the results the
+user gained in the quiz. Edges are represented by friendships.
+
+The graph can be used to identify people who can have contributed to
+the application's spreading. A method to achieve this is shown in
+figure \ref{fig:newNW}: User \textit{a} starts to use
+the application and is friend of user \textit{b}, \textit{c}, and
+\textit{d}. As user \textit{f}, and \textit{e} are only friends with
+user \textit{b}, this user contributed to the application's spreading
+very likely. It has to be mentioned that further ways exist to attract user \textit{e} or \textit{f}
+to join the application. In this paper it is assumed that virality
+is very important for the process of social transmission of an
+application. Accepting this assumption, the existence of further ways
+to attract people to participate becomes a weak argument.
+
+Identification of people such as user \textit{b} can be achieved as
+follows: At first,
+the social network of the person who started to spread the application is
+considered. For each participant, it is checked if participating
+friends exist, who are not a friend of the person who started the
+application's spreading. Those people are marked. Then, for each
+marked person their friends are analyzed almost in the same way: For
+each friend it is checked, if participating friends exist, not
+included in the list considered list of friends and not included in
+the list of friends of the person who started spreading the
+applications. If people are found, they are marked, too. This
+procedure is repeated as long as participating friends exist. In order
+to avoid an infinite searching for people, for each marked person it
+must be stored to which persons they probably spread the
+application. If a person would be added twice, no further search is
+needed within this part of the application.
+
+It can be argued, that this method of identification does not consider
+the shortest path on the graph. This is correct, but as it is not
+known how the spreading took place it does not seem rational to
+consider one path only. However, if more than one person is marked due to the
+same participants, weights computed with respect to the distance
+to the person who initialized the spreading could be used.
+
+\subsection{Implementation}
 \label{sec:implementation}
-The studied application makes use of 
-Facebook's php-\ac{sdk} and JavaScript-\ac{sdk}\footnote{http://developers.facebook.com/docs/}. It requires
-permissions (see \ref{sec:auth-auth}) for \textit{user$\_$birthday} and
-\textit{publish$\_$stream}.
+The implementation of the quiz was done using PHP, Java Script, and MySQL.
+Facebook's PHP-\ac{sdk} and
+JavaScript-\ac{sdk}\footnote{http://developers.facebook.com/docs/}
+were employed as well. The application requires
+permissions for \textit{user$\_$birthday} and
+\textit{publish$\_$stream} (see \ref{sec:auth-auth}). These
+permissions permit the application to retrieve a user's birthday and to
+send posts to a user's news stream.
+
 The questions and answers of the quiz are stored in a MySQL-database. PHP scripts
@@
 functions used by the various PHP scripts. \textit{facebook.php} and
-scripts from \textit{facebook-sdk} folder are downloaded from
+scripts from the \textit{facebook-sdk} folder are downloaded from
 \url{https://github.com/facebook/php-sdk/} provide the functionality
@@
 The view operates as follows: \textit{quiz.php} checks if the user
-completed the quiz. If not, it prints the form, loads the styles and
-includes \textit{quizQuestion.php} to print the questions. Otherwise, it
-creates the page shown after the quiz is completed by printing a
-statement commenting the user's score, and by providing users with 
-the following options: Users can print their result into their news
-stream and they can send invitations to their friends' Facebook
-profiles. For both options, Facebook's JavaScript \ac{sdk} is
+completed the quiz, and subject to this, either the quiz is shown or
+the pages containing the solution are displayed and the user is
+provided with
+the following options:  The result can be printed into the news
+stream and invitations can be send to friends' Facebook
+profiles. For both options Facebook's JavaScript \ac{sdk} is
 used. \textit{quizResult.php} contains the code to  
@@
 
-\paragraph{Database schema}
+\subsubsection{Database schema}
 \label{sec:database-schema}
-The database queries are performed with PHP
-pear\footnote{http://pear.php.net/}-package. The following tables exist:
+The database queries are performed with the 
+Pear\footnote{http://pear.php.net/} library. The following tables exist:
 \begin{itemize}
-\item \textbf{User} - entries are created for each user who participates as
-well as for each of a user's friends. A flag details if user
+\item \textbf{User} - entries are created for each participating user as
+well as for each of a user's friends. A flag details if a user
 participated or not.
 \item \textbf{Friends} - creates entries for each friendship found in
-users' friend lists.
+users' list of friends.
 \item \textbf{Questions} - contains the questions of the quiz.
 \item \textbf{Answers} - contains the possible answers and a flag to mark them
-as correct or false.
+either right or wrong.
 \item \textbf{GivenAnswers} - stores each answer given by a user.
-\item \textbf{UserScore} - stores the score user had in the quiz.
-\item \textbf{CorrectAnsweredQuestions} - stores which questions were correct
-answered by which user, and which were not.
+\item \textbf{UserScore} - stores the score a user had in the quiz.
+\item \textbf{CorrectAnsweredQuestions} - stores which questions were
+answered right by which user, and which were not.
 \end{itemize}
 
-\paragraph{Application flow}
+\subsubsection{Application flow}
 \label{sec:application-flow}
-When a user accesses the canvas page of the quiz, 
-the \textit{OAuth Dialog} is started automatically by the
-\textit{controller}. If authorization and authentication are completed
-successfully, the user's basic data as well as the birthday are stored together with
-a timestamp in the \textit{User} table. Column \textit{has-used-app} is set to 1. In
-addition, each user's friends list is also stored in \textup{User} and
-\textit{Friends} table, and for these \textit{users}, columns
+When a user accesses the canvas page of the quiz, first
+the \textit{OAuth Dialog} is executed. 
+If authorization and authentication are completed
+successfully, the user's basic data and the birthday are stored together with
+a timestamp in the \textit{User} table. Column \textit{has-used-app}
+is set to 1 if a user participated. In
+addition each user's list of table is also stored in \textup{User} and
+\textit{Friends} table and for these users column
 \textit{has-used-app} is set to 0.
@@
 % the MySQL database, checkboxes are placed before each answer. 
-Next, the quiz is created as mentioned in section
-\ref{sec:implmenetation}.
-After completion, its is evaluated the final score is computed. As
-each answer ought to be stored and multiple selection of answers is
-possible, user answers have to be stored in  a multidimensional.
-
-The given answers are then stored in table \textit{GivenAnswers}. In
-table (\textit{correctAnsweredQuestions)} it is stored which questions
-were correct or incorrect answered. This happens to spare complicated
+Afterwards the quiz is created as mentioned in section
+\ref{sec:implementation}.
+After completion, the quiz is evaluated and the final score is computed. Because
+each answer ought to be stored and multiple answers are
+possible, answers of users are stored in  a multidimensional array.
+
+The given answers are stored in table \textit{GivenAnswers}. In
+table \textit{correctAnsweredQuestions} it is stored which questions
+were answered right or wrong. This happens to spare complicated
 evaluations based on the \textit{GivenAnswers} table later on.
@@
 \label{sec:data-evaluation}
-For data evaluation, a tool coded in PHP exists. It allows for output
-of metrics as \ac{csv} and graphs in \ac{dot}
-language\footnote{http://www.graphviz.org/Documentation.php}.
-The data evaluated by the tool are taken from
- database tables the quiz also makes use of.
-
+To evaluate the data retrieved from Facebook and collected when users
+participated in the quiz  a tool was developed. It is coded in PHP and
+employs MySQL as well as the Pear library to access the
+data which were gathered when people participated in the quiz. The
+tool allows for output of metrics as \ac{csv} and graphs in \ac{dot}
+language\footnote{http://www.graphviz.org/Documentation.php}. These
+metrics are used to identify characteristics of people stored in
+the \textit{User} table. The graphs are used to visualize the whole
+process of the application's spreading. 
+Besides usage of the tool, data can also be retrieved using database
+queries. Such queries were performed to get the number of people in the user table and
+the number of people who actually participated.
+
+\subsubsection{Implementation of the tool for evaluation}
+\label{sec:impl-tool-eval}
 As mentioned in previous sections, the tool maintains an extract of
 Facebook's social graph internally. This graph contains users' basic
-information, friendships, etc. The internal graph is
-extended by information from the quiz, such as if the user has
-installed the application, and which score a user had. The internal graph
-consists of instances of class \textit{user}, which have references
-among each other representing friendships. The whole set of users is
-maintained by \textit{main.php}, which contains a list of all the user
-instances.
+information, friendships, and so forth. The internal graph is
+extended by data gained through quiz evaluations. This data includes
+information about application usage and the score the users
+received. The nodes and edges of the internal graph 
+are implemented as instances of class \textit{user}. Edges on the
+graph represent friendships. These are represented by lists of
+references to the appropriate user objects and stored as a user object
+attribute.
+The whole set of user objects is
+maintained by \textit{main.php}, where they are stored as a list.
 
@@
 results can be stored in the \textit{user} table to provide
-reusability, too. User names are made anonymous by random selection of
+reusability. User names are made anonymous by random selection of
 a name from a list of popular baby names from 2009. The list of names was
 taken from \url{http://www.ssa.gov/cgi-bin/popularnames.cgi}.   
-For each gender, hundred names are stored in an array, and if the
-gender is set, a name of same gender is chosen. Otherwise, the name is
-taken randomly. The name of the person who spread the application
-originally is always set to \textit{Alexandra}.
-
-The tool can make a prognoses, which users spread the quiz. To
-identify such users, the following idea is employed:
-A user is supposed to have spread the app if he/she has
-friends who also used the application and who belong to a \textit{new}
-social network. Figure \ref{fig:newNW} gives an example.
-The implementation is as follows: People who are supposed to have
+For each gender hundred names are stored in an array and selected
+randomly depending on the user's gender. 
+For users whose gender is not known, name and sex are set randomly. 
+The name of the person who started spreading the application
+originally is set to \textit{Alexandra} by default.
+
+The tool identifies people who can have contributed to the
+application's spreading as follows: People who are supposed to have
 spread the quiz are found by recursively checking if an user of 
-the application has friends, who also used the application, and whose friends
-also used the app, but are not in his/her list of friends, and also not in the list of the person
-who originally spread the application. In this case, the corresponding
-friend will be marked as a person who spread the application, and the
-recursion starts by letting the friend become the analyzed user.
-Since it is not clear, why a person started to use an application, the
-script also allows for identification of users who have friends 
-who also participated in the application.
-
-To let the tool output the graphs in \ac{dot} language, a parameter
+the application has participating friends whose friends also participated
+in the quiz, but are neither contained in the analyzed user's list of
+friends nor in the list of friends of the person
+who spread the application in the beginning. Then, references to the
+people to which the user is supposed to have spread the application
+are stored in a list. If a reference is added twice, the recursion is stopped.
+
+\subsubsection{Graphs and metrics the tool can put out}
+\label{sec:graphs-metrics-tool}
+In order to let the tool print the graphs in \ac{dot} language, a parameter
 has to be given to the tool via HTTP-Get method. The parameters are:
 \verb|spreading|, \verb|tree|, \verb|friendsFilled| and
-\verb|friendsScored|. If type \verb|spreading| is selected, only users
+\verb|friendsScored|. If type \verb|spreading| is selected only users
 who participated in the quiz are shown. Users who are supposed to have
-spread the application are red colored. Next to each user, the number
-of friends, and the score the user yielded in the quiz are termed. If
+spread the application get a red colored node. Beside each user its number
+of friends and the average score are mentioned. If
 type \verb|tree| is 
-selected, all the users are shown, and nodes of users who participated
-in the quiz are red colored. If type \verb|friendsFilled| is selected,
+selected all the users are shown and nodes of users who participated
+in the quiz get red colored nodes. If type \verb|friendsFilled| is selected,
 only users who participated in the quiz are considered and the
 background color is set corresponding to the number of friends. A user
-with the highest number of friends has background color black, the
+with the highest number of friends has background color black and the one
 person with the lowest number of friends has background color
-white. If type \verb|friendsScored| is selected, the graph is created
-analogous to type \verb|friendsFilled|, but the background color is
-computed with respect to the score user had in the quiz averagely.
+white. If type \verb|friendsScored| is selected the graph is created
+analogous to type \verb|friendsFilled| but the background color is
+computed with respect to the score the user had in the quiz averagely.
 
@@
 probably spread the application.  If \verb|noAppUser| is selected, it
-is only computed how many friends these user had who participated in
+is only computed how many friends these users had who participated in
 the quiz. It is returned, how many user had one friend, two friends,
 and so on.
-
-Besides the tool, some data are directly retrieved using database
-queries. These data include the number of people in the user table, and
-the number of people who participated in the application.
 
@@
 \label{sec:start-spre-proc}
-The spreading process was started by the author who posted in the news
-stream a German analogon to `please check out my new app!'. In
-addition, a message on Facebook was sent to 17 friends asking them to
-participate.
+The application is online since December 2010. On 3rd of February
+and 15th of March it was  published in the author's news stream. The
+message was posted in German and can be translated with `please check
+out my new app!'. On 2nd of March, the application was added to
+Facebook's application directory. 17 messages were sent to friends of
+the author asking them to participate. The messages were sent on
+5th and 15th of February, 3rd of March, and 1st of April. Data
+about the application's spreading were collected since the application
+was registered on Facebook.
 
@@
 \label{sec:results}
-A total of n=52 users participated in the quiz and 6311 users have been
-stored in the user table. Data were collected from 15th of February to
-15th of April. This section presents, which
-characteristics these users have based on Facebook's insights and on
-metrics computed with the tool discussed in section
-\ref{sec:data-evaluation}. Then, the graphs detailing the spreading of
-the application are shown.
+A total of n=52 users participated in the quiz and 6311 users were
+stored in the user table. In the two months after publishing, $65.38
+\%$ of the participants were friends of the author, whereas $34.63 \%$
+were not. $32.7 \%$ of the participants were invited through a message on 
+Facebook. $67.31 \%$ of the people came without a direct invitation,
+e.g. by seeing somebody use the app on their news feed.
+
+In the following passages of this section it is described which
+characteristics users had and when the application was used installed
+on used. This information is provided based on Facebook's Insights as well as
+based on metrics computed with the tool for data
+evaluation. In the end of the section,
+the graphs showing the way the application spread are shown.
 
@@
 \label{sec:characteristics}
-In this section, characteristics about the users who participated in
-the quiz are given. At first, characteristics retrieved from
+In this section characteristics about the users who participated in
+the quiz are given. In the beginning characteristics retrieved from
 Facebook's
-\textit{Insights}\footnote{http://www.facebook.com/help/?search=insights}
-are described, than, metrics collected from database and by the tool are given.
+\textit{Insights} are described.\cite{facebookInsights} Afterwards
+metrics collected from database and by the tool are given.
 
@@
 Facebook Insights `provides Facebook Page owners and Facebook Platform
-developers with metrics around their content.'\cite{facebookInsights}
-These metrics are free and can be found in the \textit{My Apps}
+developers with metrics around their content'.\cite{facebookInsights}
+These metrics can be accessed without charges. They can be found in the \textit{My Apps}
 section on the Facebook Developer Platform.
-Facebook Insights considers for its metrics life time installation of an application
-and events happened in a month. In case of the analyzed application,
-Facebook had 50 Lifetime installed users for the quiz on 15th of April, 2011.
+Facebook Insights provides metrics for specific time intervals. Users
+at specific days are distinguished from Lifetime users, who are users
+who did not uninstall the application. As two users are registered as
+developers, 50 lifetime users were found by Facebook Insights on 14th of April 2011.
 
@@
 \label{sec:age-gender}
-$60 \%$ of the registered user are female, $40 \%$ of the participants
+$60 \%$ of the registered users are female, $40 \%$ of the participants
 are male. Table \ref{tab:agegender} shows classification of the users
@@
 the age of 25-34. Few participants ($8 \%$) were older, and about a
-quarter (24 \%) were younger than 25.
+quarter (24 \%) were younger than 25. The chart given in table \ref{fig:age}
+visualizes how many participants of groups of specific ages and
+genders installed the application. In the first half of period
+analyzed, most users were male. In the second half most users were 
+female. Few participants were older than 55 or younger than 18.
+% table gender and age
+
+\paragraph{Demography}
+\label{sec:demographie}
+Table \ref{tab:countries} details where the participants are from and table
+\ref{tab:languages} presents the languages in which the participants chose
+Facebook to occur.
+
+% table about demography
+\paragraph{Internal Referrers}
+\label{sec:internal-referrers}
+Figure \ref{fig:internalRefs} shows where and how many references to the quiz 
+appeared on Facebook in the time of 1st of February 2011 to 14th of April
+2011. On 14th and 15th of February, 3rd and 6th, 17th and 27th of
+March, and 8th and 11th of April referrer to the application were
+posted in Facebook's news stream. On 4th and 7th of April the
+application was found through Facebook's search by five persons.
+
+\paragraph{Installations and Usage}
+\label{sec:user-response}
+Figure \ref{fig:installations} shows how many people used and
+installed the application in the time of 1st of February to 14th of
+April. After the first post in the news stream on 15th of February, no
+increase of installations can be found in the chart. Indeed, after the
+second post on 3rd of March, sending of invitations to users, and addition of the application to
+Facebook's directory index the number of Daily App Installations shows a
+peak. It decreased until 7th of March,
+and in the following days, only few installations took
+place. Nonetheless, the metric Daily Active Users shows that the quiz
+was repeated within these days. On 6th of April the number of
+Daily App Installations shows a third peak. This peak took part after
+the third wave of invitations. 
+Figure \ref{fig:iAs} shows the number of Daily App Installations and the
+number of Posts in the News Stream. It can be seen that posts in the
+news streams were often followed by few further installations of the application.
+Summarizing, it can be said that after each stimulus (post in the news
+stream, message to users) an increase of Daily App Installations can
+be found. Few days after such a stimulus took place usage decreased in each case.
+
+% As mentioned in section \ref{sec:start-spre-proc}, seventeen friends of the author were
+% directly invited to participate in the application. Since each of them
+% installed the application, seventeen friends of the author installed the
+% application for other reasons. The number of installations per day is
+% shown in figure \ref{fig:installations}, the data were exported from
+% Facebook Insights. A peak of new installations could be
+% found after the request to participate was posted on the news stream
+% on 3rd of March 2011. In the following days further installations
+% happened. Six of the people who were asked directly to participate
+% were not asked on 3rd of March, but afterwards. 7 people were asked
+% before.
+
+% \paragraph{Requests}
+% The quiz allows for invitation of friends to participate. For this
+% issue, users can send requests to their friends. In the time of 18th
+% of March to 8th of April four requests
+% were sent of which one was accepted. In the month before no friend
+% requests were accepted or ignored.
+
+\subsubsection{Metrics collected by the tool}
+\label{sec:tool-metrics}
+As detailed in section \ref{sec:data-evaluation}, the tool allows for
+output of metrics as \ac{csv}. Metrics about users who participated in
+the quiz are given in table
+\ref{tab:spread}. Table \ref{tab:nouser}
+describes user who did not participate. Table \ref{tab:scorespread}
+and \ref{tab:nospread} sum up metrics from table \ref{tab:spread}.
+
+From the tables it can be derived that thirty four users belonged to the
+network of the author who promoted the application in the beginning. Thus, eighteen
+application users came from other networks. Five users did not have any
+participating friends. On average, people except the author
+who had at least one \textit{app friend} had $2.5$ participating
+friends on average. People who probably spread the application to 
+one person were on average $3$ friends with who used the quiz, too. People
+who probably spread the application to two persons averagely had $5.33$
+participating friends. As it is shown in table \ref{tab:scorespread},
+the average score of people who are supposed to have contributed to
+the application's spreading was higher whenever users were supposed to have spread
+the application to more than one person.
+
+% Two tables also located in the addendum describe to how many
+% other participants ships existed (see table \ref{tab:spread} and
+% \ref{tab:nospread}), and to how many people of a
+% \textit{new} network the application was (probably) distributed by the
+% user. $26$ participants were on average $2.54$ friends with other
+% participants and those, who spread the application, seemed to have
+% more connections to other people than those who did not.
+% The average score of people connected to others was $3.02$. It was
+% higher than the average score of people not connected to others ($2.41$).
+% People not connected to further participants had fewer friends on average ($106.8$)
+% than the connected participants ($138.83$).
+
+Table \ref{tab:nouser} describes friends of participants, who did not
+participate in the quiz. As each friend was stored in the database, these people
+occur in table \textit{User} and \textit{Friends}. These people are of
+interest as they can have received friend requests
+or they may have read about the application in the news
+stream. 
+It can be obtained, that 11 users exist having 4 or five friends who
+use the application. Thus, they have more connections to application
+users than these users had on average. Indeed, most people who did not participate in the
+application were friends with less than three participants.
+
+\subsection{Graphs detailing the spreading of the quiz}
+\label{sec:distribution-quiz}
+In this section, graphs illustrating how the
+application spread are presented. The original user names collected
+from Facebook were made anonymous
+ (see section \ref{sec:data-evaluation}). Friendships are
+represented by directed edges: If user A has user B in the friend list, an
+arrow exists from A to B.
+
+Figure \ref{fig:tree} represents the graph that is created when
+parameter \verb|tree| is set. In this case, each user stored in \textit{User}
+table becomes a node, and friendships stored in table \textit{Friends}
+are represented by directed edges. Names of users who participated in the quiz are distinguished by
+red font color. The main purpose of this graph type is visualization
+of the whole spreading process. 
+The graph gives an imagination of how many 
+people on Facebook could have read about the application in their 
+news stream, or could have been invited by friends to join the
+application. In addition, the graph shows how new networks are
+reached and how dense the connections were in the network of the root
+of the spreading process.
+
+Figure \ref{fig:spreading} shows the graph that can be obtained when
+parameter \verb|spreading| is set. In this case, only users who
+participated in the quiz are considered. It can be obtained, that the
+users Evelyn, Elli, Carlos, Charlotte, David, Sebastian,
+Evan, Thomas, and Gabrielle have several connections among themselves,
+thus they belong probably to a common social network. Most people of this
+network had a relatively high score. 
+Additional smaller networks can be detected in the graph as well. One among the users Sarah, two Evans,
+and Brody, and another one among Julian, Khole, David, and Carson. In
+these networks, the application spread to people of a new network. In
+other cases, one person not connected to such a network was attracted
+to join the application. The graph also shows that besides virality,
+people not connected to the large network of participants joined the
+application, too. As five people found the application through
+Facebook search, some may refer to them.
+At least, it can be obtained that half of the people who spread the application
+had less than hundred friends, which is less than the mean on
+Facebook, i.e. 130 friends \cite{facebookStats}.
+
+% In the addendum (section \ref{sec:addendum}), two further graphs are
+% shown. In figure \ref{fig:friendsScored}, the background color
+% represents a user's average score. User with a darker background had a
+% higher score with those having a lighter background color. 
+% Figure \ref{fig:friendsFilled} visualizes the amount of friends in the
+% by giving users having many friends a dark and those having fewer
+% friends a lighter background color.
+
+% \begin{center}
+% \begin{table}
+% \label{tab:coruser}
+% \begin{tabular}{l | c c c}
+% a & a & a & a \\
+
+% \hline
+% b & b & b & b
+% \end{tabular}
+% \caption{dummy}
+% \end{table}
+% \end{center}
+
+\section{Discussion}
+\label{sec:discussion}
+In the last section, results about different topics were presented:
+The age and gender of the users, the progress of installations,
+characteristics of people who participated and who did not, and graphs
+have been shown visualizing the whole process. The number of
+people who participated was low, but this does not astonish as
+Facebook is no more as viral as it used to be. `Top application
+developers have essentially become \textit{viral growth scientists}'. \cite{facebookVirality}
+This is reflected in Zynga's application City Ville collects
+$47.9$ million users within days \cite{cityVille}, while other 
+and especially smaller firms invest money
+amounts up to $150 000$ \textdollar to promote their
+applications\cite{facebookVirality}. 
+Nonetheless, the number of 
+participants achieved with the quiz is large enough to yield interesting effects about the
+spreading in a social network nowadays.
+
+Most people who participated were in the age of twenty five to thirty
+four. This effect can be traced back to the age distribution of the
+author and the surrounding network. Another reason for the infrequent
+participation of teenagers may be further characteristics of these
+groups: Teeth from teenagers are less frequently affected with caries than older peoples' teeth
+\cite{zahngesundheit}, whereas older people use the Internet less
+frequently\cite{internetNutzung}.
+
+In section \ref{sec:internal-referrers} the internal referrers on
+Facebook were described. The number of Daily App Installations and
+Posts in the News Stream indicate that some posts in the news stream
+let to new participation, while others did not. As this effect was
+very small, it is hard to draw conclusions, anyhow. It can just be
+suggested that people with specific characteristics existed whose
+posts in the news stream attracted new participants. In case of other
+users, this did not happen.
+
+People who are supposed to have spread the application had highly differing number of
+friends (11 friends up to more than 400). Therefore, this metric can not be used to identify people who
+spread the application solely. People who had a score less than 3
+spread the application only one time. Since people can have asked
+other people to participate, this result suggests that these people
+did not invite their friends to participate. People who
+were supposed to have spread the application had a score higher than the
+average score of all participants, which is $2.84$. This effect can
+be interpret as follows: On the one hand, many people want to
+present only favourable aspects of themselves, and thus, they wanted
+their friends to find their profile picture beyond the questions.
+As users not only came by invitation, people who gained a high score
+are also likely to have a good or even admirable 
+general knowledge. If people with admirable general knowledge were also
+admired by their friends, those people's participation could make
+their friends so curious that they try the application, too.
+
+People who were supposed to have spread the application were
+friends with four other participants on average. Considering figure
+\ref{fig:installations} which shows that most installations did not
+took part after the first post on Facebook, and remembering, that
+more than one participant can have spread the application to the same
+\textit{new} participant or network, it can be hypothesized that frequent appearance
+posts coming from the same application made people curious and
+attracted them to join.
+
+Finally, it can be summarized that not only
+specific characteristics of persons who contributed to the
+application's spreading attracted new users. Indeed, further
+characteristics such as the number of participants in their network,
+the willingness to present the own person advantageously,
+frequency of posts from the application in the news stream, and particular
+interests of the group appeared to be of relevance.
+
+\section{Conclusion and outlook}
+\label{sec:conclusion}
+This research provided basic techniques for analysis of the ways in which
+applications spread on Facebook. The methodology used bases upon the
+assumption that virality plays an important role when applications
+spread on Facebook. A mechanism to identify people who contributed to
+the spreading process within their social network by analyzing an internal
+graph was presented, and results gained by its application were discussed.
+
+Results suggest that varied characteristics make users more likely to
+become a person who spreads the application. While such persons could
+not be distinguished by a particular number of friends, a user's friend's
+willingness to participate seemed to interfere with the following particularities:
+People with a worse score did not spread the application, while
+people who yielded a score clearly higher than the average did so. The
+frequency of posts in the news stream about the application and the
+number of participating friends seemed to be related to the attraction
+of new users, too. Finally, the results suggest that specific users
+exist whose posts in the news stream attracted new people to join
+the application, while post from other users do not have this effect.
+
+Future research should  analyze the described and assumed
+mechanisms more intensively and define new metrics to analyze the
+defined metrics combinatorially. Furthermore, it can be analyzed if the spreading of
+applications also allows for conclusions regarding users' positions in
+their social network. For instance, users whose post in the
+news stream sufficed solely to gain more participants could point to
+opinion leaders, while popular people may retrieve more invitations
+than other users. Than, the users' role in their social group could be
+used to gain further insight into the spreading of applications on Facebook.
+
+\include{acronym} % load acronyms
+%% \section{}
+%% \label{}
+
+%% References
+%%
+%% Following citation commands can be used in the body text:
+%% Usage of \cite is as follows:
+%%   \cite{key}          ==>>  [#]
+%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
+%%   \citet{key}         ==>>  Author [#]
+
+%% References with bibTeX database:
+
+\bibliographystyle{elsarticle-harv}
+\bibliography{literature.bib}
+
+%% Authors are advised to submit their bibtex database files. They are
+%% requested to list a bibtex style file in the manuscript if they do
+%% not want to use model1-num-names.bst.
+
+%% References without bibTeX database:
+
+% \begin{thebibliography}{00}
+
+%% \bibitem must have the following form:
+%%   \bibitem{key}...
+%%
+
+% \bibitem{}
+
+% \end{thebibliography}
+
+\newpage
+\appendix
+
+\begin{figure}
+  \includegraphics[height=3in]{../img/fbquiz.png}
+ \caption{The quiz.}
+\label{fig:quiz}
+\end{figure}
+
+\begin{figure}
+\label{fig:authorization}
+  \includegraphics[width=4in]{../img/fbinteraction3.png}
+  \caption{Facebook establishes trust relation by not sending login
+    data to app server, but using access tokens instead for
+    data exchange with app server.}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=3.5in]{../img/fbsolution.png}
+  \caption{Solution of a question.}
+\label{fig:solution}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[height=1.5in]{../img/newNW.png}
+ \caption{This figure emphasizes user b who connects the existing
+   network of users to a new social networks with
+   red border.}
+\label{fig:newNW}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=0.4in]{../img/ab.png}
+\caption{A very simple graph in \ac{dot}-language.}
+\label{fig:dot}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=0.4in]{../img/graphDot.png}
+\caption{A very simple graph with node a blue boxed and fontcolor set
+  to red.}
+\label{fig:dot2}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[height=2in]{../img/age.png}
+ \caption{This figure shows the total number of participants with
+   respect to their age and gender in the time of 1st February 2011 to
+   14th of April 2011.}
+\label{fig:age}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[height=3in]{../img/internalRefs.png}
+ \caption{This figure shows where internal references to the quiz were
+   places on Facebook in the time of 1st of February 2011 to
+   14th of April 2011.}
+\label{fig:internalRefs}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[height=3in]{../img/installAndstream.png}
+ \caption{Figure shows number of Daily App Installations and posts on
+   the news stream per day in the time of 1st of February to 14th of
+   April 2011.}
+\label{fig:iAs}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=5.2in]{../img/tree2.png}
+\caption{Figure shows all users stored in the database. Users who
+  participated have a red text color.}
+\label{fig:tree}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=5in]{../img/spreading5.png}
+\caption{Figure shows all users stored in the database. Users who
+  participated have a red text color.}
+\label{fig:spreading}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=5in]{../img/installations.png}
+\caption{Figure shows all users stored in the database. Users who
+  participated have a red text color.}
+\label{fig:installations}
+\end{figure}
+
+% \begin{figure}
+%   \includegraphics[width=3.5in]{../img/fbinvite.png}
+%   \caption{This screenshot shows how friends can be invited.}
+% \label{fig:invite}
+% \end{figure}
+
+% \begin{figure}
+%   \includegraphics[width=5in]{../img/friendsScored.png}
+% \caption{Figure shows all users stored in the database. Users who
+%   participated have a red text color.}
+% \label{fig:friendsScored}
+% \end{figure}
+
+% \begin{figure}
+%   \includegraphics[width=5in]{../img/friendsFilled.png}
+% \caption{Figure shows all users stored in the database. Users who
+%   participated have a red text color.}
+% \label{fig:friendsFilled}
+% \end{figure}
+
+\newpage
 
@@
 \begin{table}
-\label{tab:agegender}
 \begin{tabular}{l | c c c c c}
@@
 female  & 2 \% & 18 \% & 36 \% & 4 \% & 0 \%\\
-male & 0 \% & 4 \% & 32 \% & 2 \%  & 2 \\
+male & 0 \% & 4 \% & 32 \% & 2 \%  & 2 \%\\
 \end{tabular}
 \caption{Table shows classification of users by age and gender.}
+\label{tab:agegender}
 \end{table}
@@
 
-\paragraph{Demography}
-\label{sec:demographie}
-Table \ref{tab:countries} details the origin of the users and table
-\ref{tab:languages} the languages in which the participants chose
-Facebook to occur.
-
 \begin{center}
 \begin{table}
-\label{tab:countries}
 \begin{tabular}{l | c }
@@
 \caption{Table shows where the users are from.}
+\label{tab:countries}
 \end{table}
@@
 \begin{table}
-\label{tab:languages}
 \begin{tabular}{l | c }
@@
 \caption{Languages of the participants.}
+\label{tab:languages}
 \end{table}
@@
 
-\paragraph{Requests}
-The quiz allows for invitation of friends to participation by sending
-requests. In the time of 18th of March to 8th of April, 4 requests
-were sent, and one was accepted. In the month before, no friend
-requests were accepted or ignored.
-
-\subsubsection{Metrics collected by the tool}
-\label{sec:tool-metrics}
-As detailed in section \ref{sec:data-evaluation}, the tool allows for
-output of metrics as \ac{csv}. Metrics about users who participated in
-the quiz are given in table
-\ref{tab:spread}. Table \ref{tab:nouser}
-describes user who did not participate. Table \ref{tab:scorespread}
-and \ref{tab:nospread} sum up metrics from table \ref{tab:spread}.
-
-From the tables it can be derived that 34 users belonged to the
-network of the author who started to spread the application. Thus, 18
-application users came from other networks. 5 user did not have any
-friends who also participated. On average, people except the author
-and who had at least one \textit{app friend} had on average $2.5$ friends who also
-used the application. People who probably spread the application to
-one person had on average $3$ friends who used the quiz, too. People
-who probably spread to two persons had on average $5.33$ friends who
-used it, too. As it is shown in table \ref{tab:scorespread},
-the average score of people who probably spread 
-the application was higher for people who spread to more people. 
-% Two tables also located in the addendum describe to how many
-% other participants friendships existed (see table \ref{tab:spread} and
-% \ref{tab:nospread}), and to how many people of a
-% \textit{new} network the application was (probably) distributed by the
-% user. $26$ participants were on average $2.54$ friends with other
-% participants and those, who spread the application, seemed to have
-% more connections to other people than those who did not.
-% The average score of people connected to others was $3.02$. It was
-% higher than the average score of people not connected to others ($2.41$).
-% People not connected to further participants had fewer friends on average ($106.8$)
-% than the connected participants ($138.83$).
-
-Table \ref{tab:nouser} describes friends of participants, who did not
-participate in the quiz. As each friend was stored, these people also
-occur in table \textit{User} and \textit{Friends}. These friends of
-application users may have received friend requests from other users,
-and, they may have read about the application in their friends' news
-stream.
-It can be obtained, that 11 users exist having 4 or five friends who
-use the application. The larger amount of people had fewer friends who
-used the application.
-
-\subsection{User Response}
-\label{sec:user-response}
-As mentioned in section \ref{sec:start-spre-proc}, 17 friends of the author were
-directly invited to participate in the application. Each of them
-installed the application, thus 17 friends of the author installed the
-application for other reasons. The number of installations per day is
-shown in figure \ref{fig:installations}, the data were exported from
-Facebook Insights. A peak of new installations could be
-found after the request to participate was posted in the news stream
-on 3rd of March, 2011. The days after, further installations
-happened. Six of the people who were asked directly to participate,
-were not asked on 3rd of March, but afterwards. 7 people were asked
-before.
-
-\subsection{Graphs detailing the spreading of the quiz}
-\label{sec:distribution-quiz}
-In this section, graphs illustrating how the
-application spread are presented. The original user names collected
-from Facebook were made anonymous
- (see section \ref{sec:data-evaluation}). Friendships are
-represented by directed edges: If user A has user B in the friend list, an
-arrow exists targeting user B.
-
-Figure \ref{fig:allUsers} represents the graph that is created when
-parameter \verb|tree| is set. In this case, each user stored in \textit{User}
-table becomes a node, and friendships stored in table \textit{Friends}
-are represented by directed edges. Names of users who participated in the quiz are distinguished by
-red font color. The main purpose of this graph type is to
-visualization of the whole spreading process.
-The graph gives an imagination of how many 
-people on Facebook could have read about the application in their 
-news stream, or could have been invited by friends to join the
-application. In addition, the graph shows how new networks are
-reached and how dense the connections were in the network of the root
-of the spreading process.
-
-Figure \ref{fig:spreading} shows the graph that can be obtained when
-parameter \verb|spreading| is set. In this case, only users who
-participated in the quiz are considered. It can be obtained, that the
-users Evelyn, Elli, Carlos, Charlotte, David, Sebastian,
-Evan, Thomas, and Gabrielle have several connections among themselves,
-thus they belong probably to a social network. Most people of this
-network had a relatively high score. 
-Further smaller networks exist. One among the users Sarah, two Evans,
-and Brody, and another one among Julian, Khole, David, and Carson. In
-these networks, the application spread to people of a new network. In
-other cases, one new person who had a friend who used the application
-started to use it as well. In
-addition, some further people found the application in the application
-directory on Facebook.
-At least, it can be obtained that half of the people who spread the application
-had less than hundred friends, which is less than the mean on
-Facebook, i.e. 130 friends \cite{facebookStats}.
-
-% In the addendum (section \ref{sec:addendum}), two further graphs are
-% shown. In figure \ref{fig:friendsScored}, the background color
-% represents a user's average score. User with a darker background had a
-% higher score with those having a lighter background color. 
-% Figure \ref{fig:friendsFilled} visualizes the amount of friends in the
-% by giving users having many friends a dark and those having fewer
-% friends a lighter background color.
-
-% \begin{center}
-% \begin{table}
-% \label{tab:coruser}
-% \begin{tabular}{l | c c c}
-% a & a & a & a \\
-
-% \hline
-% b & b & b & b
-% \end{tabular}
-% \caption{dummy}
-% \end{table}
-% \end{center}
-
-\section{Discussion}
-\label{sec:discussion}
-From the results given in section \ref{sec:results} it can be followed
-that mainly people belonging to the author's social network
-participated in the application. Many of them came after the
-application was solicited on Facebook's news stream, but in the days
-after, further but smaller numbers of installations happened. As participation of friends was posted
-in the news streams of the participants, friends could read about the
-quiz few times. This may have made people curious about the application.
-As it can be obtained in the graphs and in the
-metrics, some users did not have friends who participated. Thus, they
-came for another reason, may be due to interest in dentistry.
-
-Most people who participated were in the age of twenty five to thirty
-four. One reason may be that most of the author's friends are of that
-age. As teenagers have less teeth affected with
-caries than people older than twenty \cite{zahngesundheit}, the chosen
-topic of the question can have increased the effect that mainly people
-in the twenties and thirties participated.
-
-From the metrics it can be concluded that the number of friends did
-not to play a bigger role in the 
-process of the application's spreading. The number of connections
-to other users and the quiz score seemed to play a bigger 
-role, as it is mentioned in section \ref{sec:tool-metrics}. 
-In addition, a worse score made people unlikely
-to spread the application, just one person with a score less than 3
-did so. Thus, people with a higher score (on average $3.11$, median $3.32$) are
-supposed to have distributed the application. Indeed, some people who
-had four or five friends who participated in the application did not
-install the application.
-
-\section{Conclusion and Outlook}
-\label{sec:conclusion}
-This research indicates that no default patterns exist describing the 
-spreading of applications on Facebook. Instead, a variety of
-factors seems to contribute to the investigated process. On the one
-hand, the application's topic limits the target group
-automatically.
-
-Beside the 
-applications topic, which limits the target group to people naturally,
-
-seem to influence this effect: On the one hand, the chosen topic of an
-application 
-people. On the other hand, their are factors such as the number of
-
-Furthermore, there
-
-. Oftentimes, people say that they don't want to
-make a worse impression on Facebook, and this is also reflected in the
-fact, that only people who yield higher scores in the quiz also
-distributed to their friends. In the environment analyzed, dense
-networks with few participants, i.e. in networks in which people know
-each other, made  further members of their network very likely to join
-the application. Indeed, the number of friends did not play a role in
-making people likely to spread the application.
-
-In order to get more reliability towards the processes of spreading
-of applications on Facebook, more applications must be analyzed.
-Future research may consider, how patterns change with respect
-to users' age, and if further characteristics can be identified. In
-case of larger applications, it could be studied, if turning points
-or intervals exist, which - when exceeded - make users significantly
-more likely to join the application.
-
-\include{acronym} % load acronyms
-%% \section{}
-%% \label{}
-
-%% References
-%%
-%% Following citation commands can be used in the body text:
-%% Usage of \cite is as follows:
-%%   \cite{key}          ==>>  [#]
-%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
-%%   \citet{key}         ==>>  Author [#]
-
-%% References with bibTeX database:
-
-\bibliographystyle{elsarticle-harv}
-\bibliography{literature.bib}
-
-%% Authors are advised to submit their bibtex database files. They are
-%% requested to list a bibtex style file in the manuscript if they do
-%% not want to use model1-num-names.bst.
-
-%% References without bibTeX database:
-
-% \begin{thebibliography}{00}
-
-%% \bibitem must have the following form:
-%%   \bibitem{key}...
-%%
-
-% \bibitem{}
-
-% \end{thebibliography}
-
 \newpage
-\section{Tables and Figures}
-\label{sec:addendum}
-
-\begin{figure}
-  \includegraphics[height=3in]{../img/fbquiz.png}
- \caption{The quiz.}
-\label{fig:quiz}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=3.5in]{../img/fbsolution.png}
-  \caption{Solution of a question.}
-\label{fig:solution}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[height=1.5in]{../img/newNW.png}
- \caption{This figure emphasizes user b who connects the existing
-   network of users to a new social networks with
-   red border.}
-\label{fig:newNW}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=5.2in]{../img/tree2.png}
-\caption{Figure shows all users stored in the database. Users who
-  participated have a red text color.}
-\label{fig:allUsers}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=5in]{../img/spreading5.png}
-\caption{Figure shows all users stored in the database. Users who
-  participated have a red text color.}
-\label{fig:spreading}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=5in]{../img/installations.png}
-\caption{Figure shows all users stored in the database. Users who
-  participated have a red text color.}
-\label{fig:installations}
-\end{figure}
-
-% \begin{figure}
-%   \includegraphics[width=3.5in]{../img/fbinvite.png}
-%   \caption{This screenshot shows how friends can be invited.}
-% \label{fig:invite}
-% \end{figure}
-
-% \begin{figure}
-%   \includegraphics[width=5in]{../img/friendsScored.png}
-% \caption{Figure shows all users stored in the database. Users who
-%   participated have a red text color.}
-% \label{fig:friendsScored}
-% \end{figure}
-
-% \begin{figure}
-%   \includegraphics[width=5in]{../img/friendsFilled.png}
-% \caption{Figure shows all users stored in the database. Users who
-%   participated have a red text color.}
-% \label{fig:friendsFilled}
-% \end{figure}
 
  \begin{table}
- \label{tab:spread}
  \begin{tabular}{ c c c c c}
@@
 Carson & 153& 3& 1 & 3 \\
-Carson & 20& 2& 1 & 3 \\
+Carson & 20& 2& 1 & 3
+
+\end{tabular}
+
+\caption{Table (part 1/2) details metrics about users who participated in the
+  application. Friends detail the number of friends a user had,
+  App-friends is the number of friends who also participated in the
+  quiz, Spread App To details to how many people a user probably
+  spread the application, and Average Score details to the score the
+  user averagely had in the quiz. The names were made anonymous.}
+ \label{tab:spread}
+\end{table}
+
+\newpage
+
+ \begin{table}
+ \begin{tabular}{ c c c c c}
+Anon. Name&Friends&App-friends&Spread App to&Average Score	\\
 Nathan & 121& 1& 0 & 4 \\
@@
 \end{tabular}
-\caption{Table details metrics about users who participated in the
+\caption{Table (part 2/2) details metrics about users who participated in the
   application. Friends detail the number of friends a user had,
@@
   user averagely had in the quiz. The names were made anonymous.}
+ \label{tab:spread2}
 \end{table}
+
+\newpage
 
@@
  \begin{table}
- \label{tab:nospread}
  \begin{tabular}{ c c}
@@
 \end{tabular}
-\caption{Table sums up metrics from table \ref{tab: spread}. It
+\caption{Table sums up metrics describing the participants. It
   details how many users had 0 friends who also participated in the
-  application, one friend, and so further.}
+  application, one friend, and so forth.}
+ \label{tab:nospread}
 \end{table}
@@
 
+ \newpage
+
 \begin{table}
-\label{tab:scorespread}
 \begin{tabular}{c c c}
@@
   concerned people.}
+\label{tab:scorespread}
 \end{table}
@@
 \begin{table}
-\label{tab:nouser}
 \begin{tabular}{c c}
@@
   participate in the application.}
+\label{tab:nouser}
 \end{table}
